---
title: "Meta_biplot"
author: "Elena Wall"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Clear things up
```{r}
rm(list = ls(all = TRUE))
graphics.off()
shell("cls")
```
My objective is to see the features that contribute to the variance in the different groupings. 
-one biplot will only look at fmt status and I must perform the biplot analysis with only those samples.
-one biplots will look at child samples and I will perform analysis only with those samples
-the final biplot would be essentially a merge that shows top features that can be found in both biplots.

load libraries
```{r}
library(cowplot)
library(qiime2R)
library(tidyverse)
library(ggsignif)
library(RColorBrewer)
library(viridis)
library(devtools)
library(ggbiplot)
library(stringr)

```
Load in data
```{r}
# load biom table
myBiom <- read_qza('./data/core-div/rarefied_table.qza')
myBiom <- as_tibble(myBiom$data, rownames = 'ASV')

myMeta <- read_tsv('./data/Keith_metadata_mapping.tsv')
# myMeta[-1,] and myMeta[2:nrow(myMeta)] are equivalent
# We want to get rid of the first row which is Qiime2 bullshit.
myMeta <- myMeta[-1,] # indexing is [row, column] 

# load in beta diversity ordinations
myWeightUniPcoa <-read_qza('./data/core-div/weighted_unifrac_pcoa_results.qza')$data
myUnweightUniPcoa <-read_qza('./data/core-div/unweighted_unifrac_pcoa_results.qza')$data
myBrayPcoa <-read_qza('./data/core-div/bray_curtis_pcoa_results.qza')$data
myJaccardPcoa <-read_qza('./data/core-div/jaccard_pcoa_results.qza')$data

weightUniProp <- myWeightUniPcoa$ProportionExplained[1:2]
unweightUniProp <- myUnweightUniPcoa$ProportionExplained[1:2]

#turn them into tibbles and stuff
myWeightUniPcoa <- as_tibble(myWeightUniPcoa$Vectors)
myUnweightUniPcoa <- as_tibble(myUnweightUniPcoa$Vectors)
myBrayPcoa <- as_tibble(myBrayPcoa$Vectors)
myJaccardPcoa <- as_tibble(myJaccardPcoa$Vectors)

colnames(myWeightUniPcoa)[1] <- '#SampleID'
colnames(myUnweightUniPcoa)[1] <- '#SampleID'
colnames(myBrayPcoa)[1] <- '#SampleID'
colnames(myJaccardPcoa)[1] <- '#SampleID'


myBiplot5 <- read_qza('./qiime/unweighted_unifrac_biplot5.qza')
myBiplot5Species <- as_tibble(myBiplot5$data$Species)
myBiplot5Vectors <- as_tibble(myBiplot5$data$Vectors)


myBiplot6 <- read_qza('./qiime/unweighted_unifrac_biplot6.qza')
myBiplot6Species <- as_tibble(myBiplot6$data$Species)
myBiplot6Vectors <- as_tibble(myBiplot6$data$Vectors)


myBiplot5Species %>% 
  mutate(FeatureID = str_replace_all(FeatureID,".*D_3", "--D_3")) ->abbrBiplot5Species


```


```{r}
#gather(-PID, -HIVID, -MSM_MSW, -Gender, -HIV_Status, -Study_Cohort, -MSM_yn, key = Markers, #value = Counts) ->myCytofBloodTidy
# prepare axis labels 
fig_1b_xaxis = paste0('PC1 (', round(unweightUniProp[1], 3) * 100, '%)')
fig_1b_yaxis = paste0('PC2 (', round(unweightUniProp[2], 3) * 100, '%)')


myUnweightUniPcoa %>% 
  select('#SampleID', PC1, PC2) -> itUnweightUniPcoa

itUnweightUniPcoa %>% 
  left_join(myMeta) ->fullerUnweightUniPcoa

fullerUnweightUniPcoa %>% 
  filter(!fmt_status == 'missing' & !fmt_status == 'NA' & 
           !fmt_status == 'noroviurus' & !fmt_status == 'vanco') -> fmtUnweightUniPcoa
  
  
#filter(grepl('CD161+', Markers) & grepl('Va7.2+', Markers) & grepl('_CD8_', Markers))

fmtUnweightUniPcoa %>% 
  ggplot(aes(PC1,PC2)) +
  geom_point(aes(fill = fmt_status),
               pch = 21, alpha=0.8, color = 'black') +
  scale_fill_brewer(palette = "Spectral")+
    theme_bw(base_size = 18) +
    xlab(fig_1b_xaxis) +
    ylab(fig_1b_yaxis) +
  ggtitle("Biplot5") -> samplePlot


  samplePlot +
    geom_segment(abbrBiplot5Species %>% 
                 mutate(a=sqrt(PC1^2+PC2^2)) %>% # calculate the distance from the origin
                 top_n(8, a) %>% #keep 8 furthest away points
                 mutate(PC1=PC1*0.3, PC2=PC2*0.3) %>% # scale arrows linearly
               aes(x=0, xend=PC1, y=0, yend=PC2, color = abbrBiplot5Species$FeatureID),
               arrow = arrow(length = unit(0.3,"cm")))



```
code modified from Jordan Bisanz
(https://forum.qiime2.org/t/how-to-make-pcoa-biplot-in-r-using-q2-deicode-ordination/8377/4)
```{r}

#create the base plot with only the arrows
fmtUnweightUniPcoa %>% 
  dplyr::rename(SampleID=`#SampleID`) -> fmtUnweightUniPcoa

abbrBiplot5Species %>% 
                 mutate(a=sqrt(PC1^2+PC2^2)) %>% # calculate the distance from the origin
                 top_n(8, a) %>% #keep 8 furthest away points
                 mutate(PC1=PC1*0.3, PC2=PC2*0.3) -> abbrBiplot5SpeciesArrows # scale arrows linearly

biplot5unweightUni <-
  ggplot() +
    theme_bw(base_size = 18) +
    xlab(fig_1b_xaxis) +
    ylab(fig_1b_yaxis) +
  ggtitle("Biplot at Taxon Level 5 by FMT status") +
  geom_point(data = fmtUnweightUniPcoa, aes( x = PC1, y = PC2, fill = fmt_status),
               pch = 21, alpha=0.8, color = 'black') +
  scale_fill_brewer(palette = "Spectral")+ 
  theme(legend.position="bottom") +  
  geom_segment(data = abbrBiplot5SpeciesArrows, aes(x=0, xend=PC1, y=0, yend=PC2,
                                                    color = FeatureID),
               arrow = arrow(length = unit(0.3,"cm")))

print(biplot5unweightUni)
```
figure out how to display taxons by arrows