---
title: "Meta_biplot"
author: "Elena Wall"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Clear things up
```{r}
rm(list = ls(all = TRUE))
graphics.off()
```
My objective is to see the features that contribute to the variance in the different groupings. 
-one biplot will only look at fmt status and I must perform the biplot analysis with only those samples.
-one biplots will look at child samples and I will perform analysis only with those samples
-the final biplot would be essentially a merge that shows top features that can be found in both biplots.

load libraries
```{r}
library(cowplot)
library(qiime2R)
library(tidyverse)
library(ggsignif)
library(RColorBrewer)
library(viridis)
library(devtools)
library(ggbiplot)
library(stringr)
library(ggrepel)

```
Load in full datasets
```{r}
# load biom table
myBiom <- read_qza('./data/core-div/rarefied_table.qza')
myBiom <- as_tibble(myBiom$data, rownames = 'ASV')

myMeta <- read_tsv('./data/Keith_metadata_mapping.tsv')
# myMeta[-1,] and myMeta[2:nrow(myMeta)] are equivalent
# We want to get rid of the first row which is Qiime2 bullshit.
myMeta <- myMeta[-1,] # indexing is [row, column] 

# load in beta diversity ordinations for full 
myWeightUniPcoa <-read_qza('./data/core-div/weighted_unifrac_pcoa_results.qza')$data
myUnweightUniPcoa <-read_qza('./data/core-div/unweighted_unifrac_pcoa_results.qza')$data


weightUniProp <- myWeightUniPcoa$ProportionExplained[1:2]
unweightUniProp <- myUnweightUniPcoa$ProportionExplained[1:2]

#turn them into tibbles and stuff
myWeightUniPcoa <- as_tibble(myWeightUniPcoa$Vectors)
myUnweightUniPcoa <- as_tibble(myUnweightUniPcoa$Vectors)

colnames(myWeightUniPcoa)[1] <- '#SampleID'
colnames(myUnweightUniPcoa)[1] <- '#SampleID'


myBiplot5 <- read_qza('./qiime/unweighted_unifrac_biplot5.qza')
myBiplot5Species <- as_tibble(myBiplot5$data$Species)
myBiplot5Vectors <- as_tibble(myBiplot5$data$Vectors)


myBiplot6 <- read_qza('./qiime/unweighted_unifrac_biplot6.qza')
myBiplot6Species <- as_tibble(myBiplot6$data$Species)
myBiplot6Vectors <- as_tibble(myBiplot6$data$Vectors)


myBiplot5Species %>% 
  mutate(FeatureID = str_replace_all(FeatureID,".*D_3__", "")) %>% 
  mutate(FeatureID = str_replace_all(FeatureID,".*D_4__", " "))->abbrBiplot5Species


```


```{r}
# prepare axis labels 
fig_1b_xaxis = paste0('PC1 (', round(unweightUniProp[1], 3) * 100, '%)')
fig_1b_yaxis = paste0('PC2 (', round(unweightUniProp[2], 3) * 100, '%)')


myUnweightUniPcoa %>% 
  select('#SampleID', PC1, PC2) -> itUnweightUniPcoa

itUnweightUniPcoa %>% 
  left_join(myMeta) ->fullerUnweightUniPcoa

fullerUnweightUniPcoa %>% 
  filter(!fmt_status == 'missing' & !fmt_status == 'NA' & 
           !fmt_status == 'noroviurus' & !fmt_status == 'vanco') -> fmtUnweightUniPcoa
  
  

fmtUnweightUniPcoa %>% 
  ggplot(aes(PC1,PC2)) +
  geom_point(aes(fill = fmt_status),
               pch = 21, alpha=0.8, color = 'black') +
  scale_fill_brewer(palette = "Spectral")+
    theme_bw(base_size = 18) +
    xlab(fig_1b_xaxis) +
    ylab(fig_1b_yaxis) +
  ggtitle("Biplot5") -> samplePlot

fmtUnweightUniPcoa %>% 
  dplyr::rename(SampleID=`#SampleID`) -> fmtUnweightUniPcoa

```
code modified from Jordan Bisanz
(https://forum.qiime2.org/t/how-to-make-pcoa-biplot-in-r-using-q2-deicode-ordination/8377/4)


```{r fig1, fig.height=7, fig.width=10}

#create the base plot with only the arrows

class(fmtUnweightUniPcoa$age)
fmtUnweightUniPcoa$age <- as.numeric(fmtUnweightUniPcoa$age)

abbrBiplot5Species %>% 
                 mutate(a=sqrt(PC1^2+PC2^2)) %>% # calculate the distance from the origin
                 top_n(5, a) %>% #keep 8 furthest away points
                 mutate(PC1=PC1*0.3, PC2=PC2*0.3) -> abbrBiplot5SpeciesArrows # scale arrows linearly

biplot5unweightUni <-
  ggplot() +
    theme_bw(base_size = 18) +
    xlab(fig_1b_xaxis) +
    ylab(fig_1b_yaxis) +
  ggtitle("Biplot at Family Level by FMT status") +
  geom_point(data = fmtUnweightUniPcoa, aes( x = PC1, y = PC2, fill = fmt_status),
               pch = 21, alpha=1, color = 'black') +
  scale_fill_viridis( discrete = TRUE) +
  labs(fill = "FMT Status") +
  theme(legend.position="bottom") + 
  geom_segment(data = abbrBiplot5SpeciesArrows, aes(x=0, xend=PC1, y=0, yend=PC2),
               arrow = arrow(length = unit(0.3,"cm")),color = 'brown2')+
  geom_text_repel(data = abbrBiplot5SpeciesArrows, aes(x=PC1, y=PC2, label=FeatureID),size=7, color = 'brown1')


print(biplot5unweightUni)
```


```{r}
#load in data for FMT studies
myWeightUniFMTPcoa <-read_qza('./qiime/Elena_data/core-metrics-metaFMT-rared-1004/weighted_unifrac_pcoa_results.qza')$data
myUnweightUniFMTPcoa <-read_qza('./qiime/Elena_data/core-metrics-metaFMT-rared-1004/unweighted_unifrac_pcoa_results.qza')$data

weightUniFMTProp <- myWeightUniFMTPcoa$ProportionExplained[1:2]
unweightUniFMTProp <- myUnweightUniFMTPcoa$ProportionExplained[1:2]

#turn them into tibbles and stuff
myWeightUniFMTPcoa <- as_tibble(myWeightUniFMTPcoa$Vectors)
myUnweightUniFMTPcoa <- as_tibble(myUnweightUniFMTPcoa$Vectors)

colnames(myWeightUniFMTPcoa)[1] <- '#SampleID'
colnames(myUnweightUniFMTPcoa)[1] <- '#SampleID'

myUnweightBiplot5FMT <- read_qza('./qiime/Elena_data/Elenas_outputs/unweighted_unifrac_FMT_biplot5.qza')
myUnweightBiplot5FMTSpecies <- as_tibble(myUnweightBiplot5FMT$data$Species)
myUnweightBiplot5FMTVectors <- as_tibble(myUnweightBiplot5FMT$data$Vectors)


myWeightBiplot5FMT <- read_qza('./qiime/Elena_data/Elenas_outputs/weighted_unifrac_FMT_biplot5.qza')
myWeightBiplot5FMTSpecies <- as_tibble(myWeightBiplot5FMT$data$Species)
myWeightBiplot5FMTVectors <- as_tibble(myWeightBiplot5FMT$data$Vectors)

myUnweightBiplot5FMTSpecies %>% 
  mutate(FeatureID = str_replace_all(FeatureID,".*D_3__", "")) %>% 
  mutate(FeatureID = str_replace_all(FeatureID,".*D_4__", " "))->abbrunWeightBiplot5FMTSpecies

myWeightBiplot5FMTSpecies %>% 
  mutate(FeatureID = str_replace_all(FeatureID,".*D_3__", "")) %>% 
  mutate(FeatureID = str_replace_all(FeatureID,".*D_4__", " "))->abbrWeightBiplot5FMTSpecies


```


```{r fig2a, fig.height=7, fig.width=10}
#WeightedFMT Biplot
# prepare axis labels 

fig_2a_xaxis = paste0('PC1 (', round(weightUniFMTProp [1], 3) * 100, '%)')
fig_2a_yaxis = paste0('PC2 (', round(weightUniFMTProp [2], 3) * 100, '%)')


myWeightUniFMTPcoa %>% 
  select('#SampleID', PC1, PC2) -> itWeightUniFMTPcoa

itWeightUniFMTPcoa %>% 
  left_join(myMeta) ->fullerWeightUniFMTPcoa

fullerWeightUniFMTPcoa %>% 
  dplyr::rename(SampleID=`#SampleID`) -> fullerWeightUniFMTPcoa

#create the base plot with only the arrows

abbrWeightBiplot5FMTSpecies %>% 
                 mutate(a=sqrt(PC1^2+PC2^2)) %>% # calculate the distance from the origin
                 top_n(5, a) %>% #keep 8 furthest away points
                 mutate(PC1=PC1*0.3, PC2=PC2*0.3) -> abbrWeightBiplot5FMTArrows # scale arrows linearly

biplot5WeightUniFMT <-
  ggplot() +
    theme_bw(base_size = 18) +
    xlab(fig_2a_xaxis) +
    ylab(fig_2a_yaxis) +
  ggtitle("Weighted Biplot at Family Level FMT Subset") +
  geom_point(data = fullerWeightUniFMTPcoa, aes( x = PC1, y = PC2, fill = fmt_status),
               pch = 21, alpha= 1, color = 'black') +
  scale_fill_viridis(discrete = TRUE, labels = c("Donor", "Post FMT", "Pre FMT")) +
  labs(fill = "FMT Status") +
  theme(legend.position="bottom") +  
  geom_segment(data = abbrWeightBiplot5FMTArrows, aes(x=0, xend=PC1, y=0, yend=PC2),
               arrow = arrow(length = unit(0.3,"cm")), color = 'brown2')+
  geom_text_repel(data = abbrWeightBiplot5FMTArrows, aes(x=PC1, y=PC2, label=FeatureID),size=5, color = 'brown1')



print(biplot5WeightUniFMT)
```

```{r fig3a, fig.height=7, fig.width=10}

# Unweighted Biplot
# prepare axis labels 
fig_2b_xaxis = paste0('PC1 (', round(unweightUniFMTProp [1], 3) * 100, '%)')
fig_2b_yaxis = paste0('PC2 (', round(unweightUniFMTProp [2], 3) * 100, '%)')


myUnweightUniFMTPcoa %>% 
  select('#SampleID', PC1, PC2) -> itUnweightUniFMTPcoa

itUnweightUniFMTPcoa %>% 
  left_join(myMeta) ->fullerUnweightUniFMTPcoa

fullerUnweightUniFMTPcoa %>% 
  dplyr::rename(SampleID=`#SampleID`) -> fullerUnweightUniFMTPcoa

#create the base plot with only the arrows

abbrunWeightBiplot5FMTSpecies %>% 
                 mutate(a=sqrt(PC1^2+PC2^2)) %>% # calculate the distance from the origin
                 top_n(5, a) %>% #keep 8 furthest away points
                 mutate(PC1=PC1*0.3, PC2=PC2*0.3) -> abbrunWeightBiplot5FMTArrows # scale arrows linearly

biplot5UnWeightUniFMT <-
  ggplot() +
    theme_bw(base_size = 18) +
    xlab(fig_2b_xaxis) +
    ylab(fig_2b_yaxis) +
  ggtitle("Unweighted Biplot at Family Level FMT Subset") +
  geom_point(data = fullerUnweightUniFMTPcoa, aes( x = PC1, y = PC2, fill = fmt_status),
               pch = 21, alpha=1, color = 'black') +
  scale_fill_viridis( direction = -1, discrete = TRUE, labels = c("Donor", "Post FMT", "Pre FMT")) +
  labs(fill = "FMT Status") +
  theme(legend.position="bottom") +  
  geom_segment(data = abbrunWeightBiplot5FMTArrows, aes(x=0, xend=PC1, y=0, yend=PC2),
               arrow = arrow(length = unit(0.3,"cm")),color = 'brown2')+
  geom_text_repel(data = abbrunWeightBiplot5FMTArrows, aes(x=PC1, y=PC2, label=FeatureID),size=7,color = 'brown1' )

print(biplot5UnWeightUniFMT)
```



```{r fig2a, fig.height=7, fig.width=10}
#Weighted Healthy

myWeightUniHealthyPcoa <-read_qza('./qiime/Elena_data/core-metrics-metaHealth-noNA-rared-1004/weighted_unifrac_pcoa_results.qza')$data

weightUniHealthyProp <- myWeightUniHealthyPcoa$ProportionExplained[1:2]

myWeightUniHealthyPcoa <- as_tibble(myWeightUniHealthyPcoa$Vectors)

colnames(myWeightUniHealthyPcoa)[1] <- '#SampleID'

myWeightBiplot5Healthy <- read_qza('./qiime/Elena_data/Elenas_outputs/weighted_unifrac_healthyNoNA_biplot5.qza')
myWeightBiplot5HealthySpecies <- as_tibble(myWeightBiplot5Healthy$data$Species)
myWeightBiplot5HealthyVectors <- as_tibble(myWeightBiplot5Healthy$data$Vectors)

myWeightBiplot5HealthySpecies %>% 
  mutate(FeatureID = str_replace_all(FeatureID,".*D_3__", "")) %>% 
  mutate(FeatureID = str_replace_all(FeatureID,".*D_4__", " "))->abbrmyWeightBiplot5HealthySpecies

#prepare axis labels
fig_3a_xaxis = paste0('PC1 (', round(weightUniHealthyProp  [1], 3) * 100, '%)')
fig_3a_yaxis = paste0('PC2 (', round(weightUniHealthyProp  [2], 3) * 100, '%)')

myWeightUniHealthyPcoa %>% 
  select('#SampleID', PC1, PC2) -> itWeightUniHealthyPcoa

itWeightUniHealthyPcoa %>% 
  left_join(myMeta) ->fullerWeightUniHealthyPcoa

fullerWeightUniHealthyPcoa %>% 
  dplyr::rename(SampleID=`#SampleID`) -> fullerWeightUniHealthyPcoa

class(fullerWeightUniHealthyPcoa$age)
fullerWeightUniHealthyPcoa$age <- as.numeric(fullerWeightUniHealthyPcoa$age)

#create the base plot with only the arrows

abbrmyWeightBiplot5HealthySpecies %>% 
                 mutate(a=sqrt(PC1^2+PC2^2)) %>% # calculate the distance from the origin
                 top_n(5, a) %>% #keep 8 furthest away points
                 mutate(PC1=PC1*0.3, PC2=PC2*0.3) -> abbrmyWeightBiplot5HealthyArrows # scale arrows linearly

biplot5WeightUniHealthy <-
  ggplot() +
    theme_bw(base_size = 18) +
    xlab(fig_3a_xaxis) +
    ylab(fig_3a_yaxis) +
  ggtitle("Weighted Biplot at Family Level Healthy Subset") +
  geom_point(data = fullerWeightUniHealthyPcoa, aes( x = PC1, y = PC2, fill = age),
               pch = 21, alpha=1, color = 'black') +
  scale_fill_viridis(direction= -1, discrete = FALSE) +
  geom_segment(data = abbrmyWeightBiplot5HealthyArrows, aes(x=0, xend=PC1, y=0, yend=PC2),
               arrow = arrow(length = unit(0.3,"cm")),color = 'brown2')+
  geom_text_repel(data = abbrmyWeightBiplot5HealthyArrows, aes(x=PC1, y=PC2, label=FeatureID),size=5,color = 'brown1')+
  labs(fill = "Age") +  
  theme_bw()
  
print(biplot5WeightUniHealthy)
```

```{r fig3b, fig.height=7, fig.width=10}
#Unweighted Healthy
myUnweightUniHealthyFMTPcoa <-read_qza('./qiime/Elena_data/core-metrics-metaHealth-noNA-rared-1004/unweighted_unifrac_pcoa_results.qza')$data

unweightUniHealthyProp <- myUnweightUniHealthyFMTPcoa$ProportionExplained[1:2]

myUnweightUniHealthyFMTPcoa  <- as_tibble(myUnweightUniHealthyFMTPcoa$Vectors)

colnames(myUnweightUniHealthyFMTPcoa)[1] <- '#SampleID'

myUnweightBiplot5Healthy <- read_qza('./qiime/Elena_data/Elenas_outputs/unweighted_unifrac_healthyNoNA_biplot5.qza')
myUnweightBiplot5HealthySpecies <- as_tibble(myUnweightBiplot5Healthy$data$Species)
myUnweightBiplot5HealthyVectors <- as_tibble(myUnweightBiplot5Healthy$data$Vectors)

myUnweightBiplot5HealthySpecies %>% 
  mutate(FeatureID = str_replace_all(FeatureID,".*D_3__", "")) %>% 
  mutate(FeatureID = str_replace_all(FeatureID,".*D_4__", " "))->abbrUnweightBiplot5HealthySpecies

#prepare axis labels
fig_3b_xaxis = paste0('PC1 (', round(unweightUniHealthyProp  [1], 3) * 100, '%)')
fig_3b_yaxis = paste0('PC2 (', round(unweightUniHealthyProp  [2], 3) * 100, '%)')

myUnweightUniHealthyFMTPcoa %>% 
  select('#SampleID', PC1, PC2) -> itUnweightUniHealthyFMTPcoa

itUnweightUniHealthyFMTPcoa %>% 
  left_join(myMeta) ->fullerUnweightUniHealthyFMTPcoa

fullerUnweightUniHealthyFMTPcoa %>% 
  dplyr::rename(SampleID=`#SampleID`) -> fullerUnweightUniHealthyFMTPcoa

class(fullerUnweightUniHealthyFMTPcoa$age)
fullerUnweightUniHealthyFMTPcoa$age <- as.numeric(fullerUnweightUniHealthyFMTPcoa$age)

#create the base plot with only the arrows

abbrUnweightBiplot5HealthySpecies %>% 
                 mutate(a=sqrt(PC1^2+PC2^2)) %>% # calculate the distance from the origin
                 top_n(5, a) %>% #keep 8 furthest away points
                 mutate(PC1=PC1*0.3, PC2=PC2*0.3) -> abbrUnweightBiplot5HealthyArrows # scale arrows linearly

biplot5UnWeightUniHealthy <-
  ggplot() +
    theme_bw(base_size = 18) +
    xlab(fig_3b_xaxis) +
    ylab(fig_3b_yaxis) +
  ggtitle("Unweighted Biplot at Family Level Healthy Subset") +
  geom_point(data = fullerUnweightUniHealthyFMTPcoa, aes( x = PC1, y = PC2, fill = age),
               pch = 21, alpha=1, color = 'black') +
  scale_fill_viridis(direction = -1,  discrete =FALSE) +
  guides(fill =guide_colourbar(label.position = "right"))+
  labs(fill = "Age") +
  geom_segment(data = abbrUnweightBiplot5HealthyArrows, aes(x=0, xend=PC1, y=0, yend=PC2),
               arrow = arrow(length = unit(0.3,"cm")),color = 'brown2')+
  geom_text_repel(data = abbrUnweightBiplot5HealthyArrows, aes(x=PC1, y=PC2, label=FeatureID),size=7,color = 'brown1')

print(biplot5UnWeightUniHealthy)
```

```{r fig.height=17, fig.width=20}
plot_grid(biplot5unweightUni, biplot5UnWeightUniFMT, biplot5UnWeightUniHealthy,
          nrow = 2, labels = c('a', 'b', 'c'),
          label_size = 22,
          rel_heights = c(1, 1)) -> fig_1

print(fig_1)

```

```{r}
library(scales)
show_col(viridis_pal(option = "viridis")(20))
q_colors =  3 # for no particular reason
v_colors =  viridis(q_colors, option ="magma")

#FD9A6AF, 
```


