---
title: "Meta-SS"
author: "Elena Wall"
date: "`r Sys.Date()`"
output: html_document
---

```{r, echo=FALSE}
library(broom)
library(cowplot)
library(ggplot2)
library(qiime2R)
library(tidyverse)
library(rstatix)
library(ggpubr)
library(ggpmisc)
library(ggforce)
library(lme4)
library(viridis)
library(cluster)
library(dplyr)
library(farver)
library(grateful)
library(phyloseq)
library(microshades)
library(gt)
library(rcompanion)
library(speedyseq)
library(purrr)
library(patchwork)
library(ggsignif)
library(RColorBrewer)
library(ggnewscale)

library(NbClust)
library(Silhouette)
library(proxy)

#cite_packages(output = "paragraph", out.dir = "~/Desktop/Lozupone_022425/Keith/Metaanalysis/")
```

```{r}
myMeta <- read_tsv('~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/metaMappingEW_KZHFiltered4.tsv')

myMeta <- as_tibble(myMeta)
colnames(myMeta)[1]<-"SampleID"

```
Going back to using metadata categories for enterotyping, so will need to use the subsetted core-diversity metrics from the 
```{r}
##
## Unweighted All
myUnweightUniFullPcoa <-read_qza('~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/core-metrics-OriginalMeta2-caseyFiltered-rared-1004/unweighted_unifrac_pcoa_results.qza')$data
#get axis info
unweightUniFullProp <- myUnweightUniFullPcoa$ProportionExplained[1:4]

#unweighted full prepare axis labels 
unweighted1_xaxis = paste0('PC1 (', round(unweightUniFullProp[1], 3) * 100, '%)')
unweighted2_yaxis = paste0('PC2 (', round(unweightUniFullProp[2], 3) * 100, '%)')
unweighted3_yaxis = paste0('PC3 (', round(unweightUniFullProp[3], 3) * 100, '%)')
unweighted4_yaxis = paste0('PC4 (', round(unweightUniFullProp[4], 3) * 100, '%)')

#turn them into tibbles and stuff
myUnweightUniFullPcoa <- as_tibble(myUnweightUniFullPcoa$Vectors)

colnames(myUnweightUniFullPcoa)[1] <- 'SampleID'
colnames(myUnweightUniFullPcoa)[2] <- 'PC1_UnWt'
colnames(myUnweightUniFullPcoa)[3] <- 'PC2_UnWt'
colnames(myUnweightUniFullPcoa)[4] <- 'PC3_UnWt'
colnames(myUnweightUniFullPcoa)[5] <- 'PC4_UnWt'

# reducing data if needed
myUnweightUniFullPcoa %>% 
  select(SampleID,PC1_UnWt, PC2_UnWt, PC3_UnWt, PC4_UnWt) ->lessUnweightedPCoA

rm(myUnweightUniFullPcoa, unweightUniFullProp)

myMeta %>% 
  left_join(lessUnweightedPCoA) ->fullerunWeightUniFullPcoa
#write_tsv(fullerunWeightUniFullPcoa, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/  unweightedPC123withMeta.tsv", quote = "none")
```
use metrics of each clusters fit to set threshold for "well clustered" samples
within PAM object is a clusinfo data table that can tell max and avg dissimilarity between the observations in the cluster and the cluster's medoid
also may be useful to use diameter of the cluster (maximal dissimilarity between two observations of the cluster)
```{r}
ClusteringSummary <-function(weightClusterNum, ClusterNumString, sil_max, sil_min, neighbor_thresh,unclust_thresh) 
  {

weightClusterNum$clusinfo->dis
dis %>% 
  as.tibble() ->dis

dis %>% 
  dplyr::summarise(across(where(is.numeric), mean, na.rm = TRUE)) %>% 
  round(., digits = 4)->sum

t(sum)->txSum
txSum<-as_tibble(txSum, rownames = "metric")
txSum %>% 
  filter(metric != "Cluster")->txSum
colnames(txSum)[2] <- 'mean'
txSum$mean <- as.character(txSum$mean)

dis$Cluster <- rownames(dis)
dis$Scheme <- ClusterNumString
dis$Cluster <-as.numeric(dis$Cluster)
dis %>%
  as.tibble() %>% 
  gather(-Scheme, -Cluster, key=metric, value = unit)->tidyDiss

dis %>% 
   pull(Cluster, name = Cluster)->labelVector

weightClusterNum$silinfo$widths->AllSilWidths
AllSilWidths %>% 
  as.tibble() ->AllSilWidths

weightClusterNum$silinfo$avg.width->AvgSilWidth

sum %>% 
    mutate(TotalAvgSW = AvgSilWidth)->sum

tidyDiss %>% 
  ggplot()+
  geom_point(aes(x=Cluster, y=unit))+
  scale_x_discrete(limits=labelVector)+
  facet_wrap(~metric, scale = 'free_y',labeller = as_labeller(c(
  'av_diss' = "avg. dissimilarity from medoid",
  'diameter'= "diameter of cluster",
  'max_diss' ="max. dissimilarity from medoid",
  'separation' = "min. seperation of two cluster observations",
  'size' = "number of observations")))+
  geom_text(data = txSum, aes(x = Inf, y = Inf,
                              hjust = 1, vjust = 1,
                              label = mean))+
  ggtitle(ClusterNumString)->SummaryPlot

AllSilWidths %>%
  group_by(cluster) %>%
  dplyr::summarise(mean = mean(sil_width), n = n()) %>% 
  mutate(isLow = mean < 0.1) %>% 
  mutate(label =paste(cluster, "(",n,")", ":", mean))->OrigAvgSil
 
percentLow <- (sum(OrigAvgSil$isLow))/(max(row_number(OrigAvgSil)))

OrigAvgSil %>% 
   pull(label, name = cluster)->labelOrig

weightClusterNum$silinfo$widths->AllSilWidths
AllSilWidths<-as_tibble(AllSilWidths, rownames = "SampleID")
AllSilWidths$cluster <- as.factor(AllSilWidths$cluster)
AllSilWidths %>% 
  arrange(cluster,sil_width)->OrderedSilWidths

OrderedSilWidths %>% 
  mutate(id = row_number()) %>% 
  ggplot(aes(fill = cluster, x=id, y=sil_width))+
  geom_col(width = 1)+
    facet_grid(~cluster, switch = "x", scales = "free_x", space = "free_x") +
    scale_fill_discrete(labels = labelOrig)+
    theme_minimal() +
    theme(axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside") + 
    xlab("Cluster")+
  ggtitle(ClusterNumString)->ClusterSil

#make a refined Cluster assignment

OrderedSilWidths %>% 
  mutate(RefinedClusters = case_when(sil_width < 0.10 ~ "12",
                             TRUE ~ cluster)) ->RefinedOrdSilWidths

RefinedOrdSilWidths %>% 
  select(SampleID,RefinedClusters) ->ReDefinedClusters

matchedRedefinedClusters <- ReDefinedClusters[match(rownames(as.matrix(weightClusterNum$diss)), ReDefinedClusters$SampleID), ]
#cluster 5 maintains only 
matchedRedefinedClusters %>% 
  mutate(RefinedClusters = case_when(RefinedClusters == "5" ~ "12",
                             TRUE ~ RefinedClusters)) %>%  
   pull(RefinedClusters, name = SampleID) ->namedReAssignmentVector 
namedReAssignmentVector %>%
  as.integer()->reAssignmentVector

reClusterSil<- silhouette(reAssignmentVector, weightClusterNum$diss)
rownames(reClusterSil)<-names(namedReAssignmentVector )

reClusterSil %>% 
  as_tibble(rownames = "SampleID")->reClusterSWTable
colnames(reClusterSWTable)[2] <- 'RefinedClusters'

reClusterSWTable$RefinedClusters <- as.factor(reClusterSWTable$RefinedClusters)
reClusterSWTable %>% 
    mutate(RefinedClusters = case_when(RefinedClusters == "12" ~ "unClustered",
                             TRUE ~ RefinedClusters))->reClusterSWTable

levelVector <- c(labelVector, "unClustered")

reClusterSWTable$RefinedClusters<- factor(reClusterSWTable$RefinedClusters, levels = c(levelVector))

reClusterSWTable %>% 
  arrange(RefinedClusters,sil_width) ->OrdRefSilWidths

OrdRefSilWidths %>%
  group_by(RefinedClusters) %>%
  dplyr::summarise(mean = mean(sil_width), n = n()) %>% 
  mutate(label =paste(RefinedClusters, "(",n,")", ":", mean))->RefinedAvgSil

RefinedAvgSil %>% 
   pull(label, name = RefinedClusters)->labelRefined

OrdRefSilWidths %>% 
  mutate(id = row_number()) %>% 
  ggplot(aes(fill = RefinedClusters, x=id, y=sil_width))+
  geom_col(width = 1)+
    facet_grid(~RefinedClusters, switch = "x", scales = "free_x", space = "free_x") +
    scale_fill_discrete(labels = labelRefined)+
    theme_minimal() +
    theme(axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside") + 
    xlab("RefinedClusters")+
  ggtitle(ClusterNumString)->RefClusterSil

OrdRefSilWidths %>% 
  select(SampleID,RefinedClusters) ->ReRefinedClusters

OrdRefSilWidths %>% 
  filter(RefinedClusters == "unClustered") %>% 
  select(SampleID)->unClusteredSamples

##make a Neighbor Clustering
AllSilWidths$neighbor <-as.character(AllSilWidths$neighbor)
AllSilWidths %>% 
  mutate(ReNeighborClusters = case_when(
                            sil_width < sil_max & sil_width > sil_min ~ "12",
                            sil_width < neighbor_thresh ~  neighbor,
                             TRUE ~ cluster)) ->RefinedNeighborSilWidths

RefinedNeighborSilWidths %>% 
  select(SampleID,ReNeighborClusters) ->ReDefNeighborClusters

matchedNeighborClusters <- ReDefNeighborClusters[match(rownames(as.matrix(weightClusterNum$diss)), ReDefNeighborClusters$SampleID), ]

matchedNeighborClusters %>% 
  mutate(ReNeighborClusters = case_when(#ReNeighborClusters == "5" ~ "12",
                             TRUE ~ ReNeighborClusters)) %>%  
   pull(ReNeighborClusters, name = SampleID) ->neighmedAssignmentVector 
neighmedAssignmentVector  %>%
  as.integer()->AssignmentVector

NeighborSil<- silhouette(AssignmentVector, weightClusterNum$diss)
rownames(NeighborSil)<-names(neighmedAssignmentVector )

NeighborSil %>% 
  as_tibble(rownames = "SampleID")->NeighborSWTable
colnames(NeighborSWTable)[2] <- 'ReNeighborClusters'

NeighborSWTable$ReNeighborClusters <- as.factor(NeighborSWTable$ReNeighborClusters)
NeighborSWTable %>% 
    mutate(ReNeighborClusters = case_when(ReNeighborClusters == "12" ~ "unClustered",
                             TRUE ~ ReNeighborClusters))->NeighborSWTable
NeighborSWTable$ReNeighborClusters <- factor(NeighborSWTable$ReNeighborClusters, levels = c(levelVector))
NeighborSWTable %>% 
  arrange(ReNeighborClusters,sil_width) ->OrdNeighborNewSWs

OrdNeighborNewSWs %>%
  group_by(ReNeighborClusters) %>%
  dplyr::summarise(mean = mean(sil_width), n = n()) %>% 
  mutate(label =paste(ReNeighborClusters, "(",n,")", ":", mean)) %>% 
  ungroup()->NeighborAvgSil

NeighborAvgSil %>% 
   pull(label, name = ReNeighborClusters)->labelNewNeigh

OrdNeighborNewSWs %>% 
  mutate(id = row_number()) %>% 
  ggplot(aes(fill = ReNeighborClusters, x=id, y=sil_width))+
  geom_col(width = 1)+
    facet_grid(~ReNeighborClusters, switch = "x", scales = "free_x", space = "free_x") +
    scale_fill_discrete(labels = labelNewNeigh)+
    theme_minimal() +
    theme(axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside") + 
    xlab("ReNeighborClusters")+
  ggtitle(ClusterNumString)->newNeighborSilPlot

##make poor Neighbors into unclustered
OrdNeighborNewSWs$neighbor <-as.character(OrdNeighborNewSWs$neighbor)
OrdNeighborNewSWs %>% 
  mutate(unNeighborClusters = case_when(sil_width < unclust_thresh & ReNeighborClusters != "unClustered" ~"12",
                                         ReNeighborClusters == "unClustered" ~ "12",
                             TRUE ~ ReNeighborClusters)) ->unNeighborSilWidths

unNeighborSilWidths %>% 
  select(SampleID,unNeighborClusters) ->unClustNeighborClusters

matchedUnNeighborClusters <- unClustNeighborClusters[match(rownames(as.matrix(weightClusterNum$diss)), unClustNeighborClusters$SampleID), ]

matchedUnNeighborClusters %>% 
   pull(unNeighborClusters, name = SampleID) ->unNeighmedAssignmentVector 
unNeighmedAssignmentVector  %>%
  as.integer()->unNeighborAssignmentVector

unNeighborSil<- silhouette(unNeighborAssignmentVector, weightClusterNum$diss)
rownames(unNeighborSil)<-names(unNeighmedAssignmentVector)

unNeighborSil %>% 
  as_tibble(rownames = "SampleID")->unNeighborSWTable
colnames(unNeighborSWTable)[2] <- 'unNeighborClusters'

unNeighborSWTable$unNeighborClusters <- as.factor(unNeighborSWTable$unNeighborClusters)
unNeighborSWTable %>% 
    mutate(unNeighborClusters = case_when(unNeighborClusters == "12" ~ "unClustered",
                             TRUE ~ unNeighborClusters))->unNeighborSWTable
unNeighborSWTable$unNeighborClusters <- factor(unNeighborSWTable$unNeighborClusters, levels = c(levelVector))
unNeighborSWTable %>% 
  arrange(unNeighborClusters,sil_width) ->OrdUnNeighborNewSWs

OrdUnNeighborNewSWs %>%
  group_by(unNeighborClusters) %>%
  dplyr::summarise(mean = mean(sil_width), n = n()) %>% 
  mutate(label =paste(unNeighborClusters, "(",n,")", ":", mean)) %>% 
  ungroup()->unNeighborAvgSil

unNeighborAvgSil %>% 
   pull(label, name = unNeighborClusters)->labelUnNeigh

OrdUnNeighborNewSWs %>% 
  mutate(id = row_number()) %>% 
  ggplot(aes(fill = unNeighborClusters, x=id, y=sil_width))+
  geom_col(width = 1)+
    facet_grid(~unNeighborClusters, switch = "x", scales = "free_x", space = "free_x") +
    scale_fill_discrete(labels = labelUnNeigh)+
    theme_minimal() +
    theme(axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside") + 
    xlab("redone Neighbor Clusters")+
  ggtitle(ClusterNumString)->unNeighborSilPlot

OrdUnNeighborNewSWs %>% 
  filter(unNeighborClusters == "unClustered") %>% 
  select(SampleID)->lowClusteredSamples

  return(list(SummaryPlot=SummaryPlot,
              SilhouetteTable=AllSilWidths,
              AverageSilWidth=OrigAvgSil,
              DistanceSummary = sum ,
              SumSpecifics = tidyDiss,
              PercentLowClusters = percentLow,
              ClusterSilPlot=ClusterSil,
              RefinedClustersSil = OrdRefSilWidths,
              RefClusterSilPlot=RefClusterSil,
              RefAvgSilWidths=RefinedAvgSil,
              RedefinedClusters = ReRefinedClusters,
              NeighborClusterNewSW = OrdNeighborNewSWs,
              RefNeighborClusterSilPlot=newNeighborSilPlot,
              RefAvgNeighborSW=NeighborAvgSil,
              RedefinedNeighborClusters = ReDefNeighborClusters,
              newSampleList = unClusteredSamples,
              redoneNeighborsSWs = OrdUnNeighborNewSWs,
              redoneNeighborsSWPlot = unNeighborSilPlot,
              redoneNeighborAvgSW=unNeighborAvgSil,
              lowClustered = lowClusteredSamples))
}
```

Dysbio Cluster
```{r}
## load in weightUNI dysbio distance matrix
myWeightUnipreFMTDM <-read_qza('~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/core-metrics_MetaAnalysis_preFMT-1004/weighted_unifrac_distance_matrix.qza')$data


#Partitioning (clustering) of the data into k clusters “around medoids”, a more robust version of K-means.
weightClusterDysbioAdults2 <- pam(myWeightUnipreFMTDM,2, keep.diss = TRUE)
clusterWeightDysbioAdult2 <- pam(myWeightUnipreFMTDM,2, cluster.only = TRUE)

weightClusterDysbioAdults3 <- pam(myWeightUnipreFMTDM,3, keep.diss = TRUE)
clusterWeightDysbioAdult3 <- pam(myWeightUnipreFMTDM,3, cluster.only = TRUE)

weightClusterDysbioAdults4 <- pam(myWeightUnipreFMTDM,4, keep.diss = TRUE)
clusterWeightDysbioAdult4 <- pam(myWeightUnipreFMTDM,4, cluster.only = TRUE)

weightClusterDysbioAdults5 <- pam(myWeightUnipreFMTDM,5, keep.diss = TRUE)
clusterWeightDysbioAdult5 <- pam(myWeightUnipreFMTDM,5, cluster.only = TRUE)

weightClusterDysbioAdults6 <- pam(myWeightUnipreFMTDM,6, keep.diss = TRUE)
clusterWeightDysbioAdult6 <- pam(myWeightUnipreFMTDM,6, cluster.only = TRUE)

weightClusterDysbioAdults7 <- pam(myWeightUnipreFMTDM,7, keep.diss = TRUE)
clusterWeightDysbioAdult7 <- pam(myWeightUnipreFMTDM,7, cluster.only = TRUE)

weightClusterDysbioAdults8 <- pam(myWeightUnipreFMTDM,8, keep.diss = TRUE)
clusterWeightDysbioAdult8 <- pam(myWeightUnipreFMTDM,8, cluster.only = TRUE)

weightClusterDysbioAdults9 <- pam(myWeightUnipreFMTDM,9, keep.diss = TRUE)
clusterWeightDysbioAdult9 <- pam(myWeightUnipreFMTDM,9, cluster.only = TRUE)

weightClusterDysbioAdults10 <- pam(myWeightUnipreFMTDM,10, keep.diss = TRUE)
clusterWeightDysbioAdult10 <- pam(myWeightUnipreFMTDM,10, cluster.only = TRUE)

weightClusterDysbioAdults11 <- pam(myWeightUnipreFMTDM,11, keep.diss = TRUE)
clusterWeightDysbioAdult11 <- pam(myWeightUnipreFMTDM,11, cluster.only = TRUE)

weightClusterDysbioAdults12 <- pam(myWeightUnipreFMTDM,12, keep.diss = TRUE)
clusterWeightDysbioAdult12 <- pam(myWeightUnipreFMTDM,12, cluster.only = TRUE)

weightClusterDysbioAdults13 <- pam(myWeightUnipreFMTDM,13, keep.diss = TRUE)
clusterWeightDysbioAdult13 <- pam(myWeightUnipreFMTDM,13, cluster.only = TRUE)

weightClusterDysbioAdults14 <- pam(myWeightUnipreFMTDM,14, keep.diss = TRUE)
clusterWeightDysbioAdult14 <- pam(myWeightUnipreFMTDM,14, cluster.only = TRUE)

weightClusterDysbioAdults15 <- pam(myWeightUnipreFMTDM,15, keep.diss = TRUE)
clusterWeightDysbioAdult15 <- pam(myWeightUnipreFMTDM,15, cluster.only = TRUE)

weightClusterDysbioAdults16 <- pam(myWeightUnipreFMTDM,16, keep.diss = TRUE)
clusterWeightDysbioAdult16 <- pam(myWeightUnipreFMTDM,16, cluster.only = TRUE)


DysbioCluster2Stats<-ClusteringSummary(weightClusterDysbioAdults2, "Clusters_2",NA,NA,NA,NA)
DysbioCluster3Stats<-ClusteringSummary(weightClusterDysbioAdults3, "Clusters_3",NA,NA,NA,NA)
DysbioCluster4Stats<-ClusteringSummary(weightClusterDysbioAdults4, "Clusters_4",NA,NA,NA,NA)
DysbioCluster5Stats<-ClusteringSummary(weightClusterDysbioAdults5, "Clusters_5",NA,NA,NA,NA)
DysbioCluster6Stats<-ClusteringSummary(weightClusterDysbioAdults6, "Clusters_6",NA,NA,NA,NA)
DysbioCluster7Stats<-ClusteringSummary(weightClusterDysbioAdults7, "Clusters_7",NA,NA,NA,NA)
DysbioCluster8Stats<-ClusteringSummary(weightClusterDysbioAdults8, "Clusters_8",NA,NA,NA,NA)
DysbioCluster9Stats<-ClusteringSummary(weightClusterDysbioAdults9, "Clusters_9",NA,NA,NA,NA)
DysbioCluster10Stats<-ClusteringSummary(weightClusterDysbioAdults10, "Clusters_10",NA,NA,NA,NA)
DysbioCluster11Stats<-ClusteringSummary(weightClusterDysbioAdults11, "Clusters_11",NA,NA,NA,NA)
DysbioCluster12Stats<-ClusteringSummary(weightClusterDysbioAdults12, "Clusters_12",NA,NA,NA,NA)
DysbioCluster13Stats<-ClusteringSummary(weightClusterDysbioAdults13, "Clusters_13",NA,NA,NA,NA)
DysbioCluster14Stats<-ClusteringSummary(weightClusterDysbioAdults14, "Clusters_14",NA,NA,NA,NA)
DysbioCluster15Stats<-ClusteringSummary(weightClusterDysbioAdults15, "Clusters_15",NA,NA,NA,NA)
DysbioCluster16Stats<-ClusteringSummary(weightClusterDysbioAdults16, "Clusters_16",NA,NA,NA,NA)
```

```{r, fig.width=13, fig.height =6}
Dysbio2<-DysbioCluster2Stats$DistanceSummary
Dysbio2$DysbioClusters <- "2"
Dysbio3<-DysbioCluster3Stats$DistanceSummary
Dysbio3$DysbioClusters <- "3"
Dysbio4<-DysbioCluster4Stats$DistanceSummary
Dysbio4$DysbioClusters <- "4"
Dysbio5<-DysbioCluster5Stats$DistanceSummary
Dysbio5$DysbioClusters <- "5"
Dysbio6<-DysbioCluster6Stats$DistanceSummary
Dysbio6$DysbioClusters <- "6"
Dysbio7<-DysbioCluster7Stats$DistanceSummary
Dysbio7$DysbioClusters <- "7"
Dysbio8<-DysbioCluster8Stats$DistanceSummary
Dysbio8$DysbioClusters <- "8"
Dysbio9<-DysbioCluster9Stats$DistanceSummary
Dysbio9$DysbioClusters <- "9"
Dysbio10<-DysbioCluster10Stats$DistanceSummary
Dysbio10$DysbioClusters <- "10"
Dysbio11<-DysbioCluster11Stats$DistanceSummary
Dysbio11$DysbioClusters <- "11"
Dysbio12<-DysbioCluster12Stats$DistanceSummary
Dysbio12$DysbioClusters <- "12"
Dysbio13<-DysbioCluster13Stats$DistanceSummary
Dysbio13$DysbioClusters <- "13"
Dysbio14<-DysbioCluster14Stats$DistanceSummary
Dysbio14$DysbioClusters <- "14"
Dysbio15<-DysbioCluster15Stats$DistanceSummary
Dysbio15$DysbioClusters <- "15"
Dysbio16<-DysbioCluster16Stats$DistanceSummary
Dysbio16$DysbioClusters <- "16"

lowList<-c(DysbioCluster2Stats$PercentLowClusters,
           DysbioCluster3Stats$PercentLowClusters,
          DysbioCluster4Stats$PercentLowClusters,
          DysbioCluster5Stats$PercentLowClusters,
          DysbioCluster6Stats$PercentLowClusters,
          DysbioCluster7Stats$PercentLowClusters,
          DysbioCluster8Stats$PercentLowClusters,
          DysbioCluster9Stats$PercentLowClusters,
          DysbioCluster10Stats$PercentLowClusters,
          DysbioCluster11Stats$PercentLowClusters,
          DysbioCluster12Stats$PercentLowClusters,
          DysbioCluster13Stats$PercentLowClusters,
          DysbioCluster14Stats$PercentLowClusters,
          DysbioCluster15Stats$PercentLowClusters,
          DysbioCluster16Stats$PercentLowClusters)

DysbioClusters<-c("2","3","4","5","6",
              "7","8","9","10","11",
              "12","13","14","15","16")

lowTableDysbio<-tibble(DysbioClusters,lowList)

Dysbio2 %>% 
  full_join(Dysbio3) %>% 
  full_join(Dysbio4) %>% 
  full_join(Dysbio5) %>% 
  full_join(Dysbio6) %>% 
  full_join(Dysbio7) %>% 
  full_join(Dysbio8) %>% 
  full_join(Dysbio9) %>% 
  full_join(Dysbio10) %>% 
  full_join(Dysbio11) %>% 
  full_join(Dysbio12) %>% 
  full_join(Dysbio13) %>% 
  full_join(Dysbio14) %>% 
  full_join(Dysbio15)%>% 
  full_join(Dysbio16)->DysbioStats

lowTableDysbio %>% 
  left_join(DysbioStats) ->DysbioSummaryTable

write_tsv(DysbioSummaryTable, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/dysbioLowList_082926.tsv", quote = "none")
#11 has the lower Percent (.18) of clusters with avg sil widths less than 0.1

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/DysbioClusterSummary_082926.pdf", width = 13, height = 11)
DysbioCluster2Stats$SummaryPlot
DysbioCluster6Stats$SummaryPlot
DysbioCluster5Stats$SummaryPlot
DysbioCluster11Stats$SummaryPlot
DysbioCluster12Stats$SummaryPlot
DysbioCluster10Stats$SummaryPlot
DysbioCluster2Stats$ClusterSilPlot
DysbioCluster6Stats$ClusterSilPlot
DysbioCluster5Stats$ClusterSilPlot
DysbioCluster11Stats$ClusterSilPlot
DysbioCluster12Stats$ClusterSilPlot
DysbioCluster10Stats$ClusterSilPlot
DysbioCluster2Stats$RefClusterSilPlot
DysbioCluster6Stats$RefClusterSilPlot
DysbioCluster5Stats$RefClusterSilPlot
DysbioCluster11Stats$RefClusterSilPlot
DysbioCluster12Stats$RefClusterSilPlot
DysbioCluster10Stats$RefClusterSilPlot
DysbioCluster2Stats$RefNighborClusterSilPlot
DysbioCluster11Stats$RefNighborClusterSilPlot
DysbioCluster12Stats$RefNighborClusterSilPlot
DysbioCluster10Stats$RefNighborClusterSilPlot
DysbioCluster6Stats$RefNighborClusterSilPlot
DysbioCluster5Stats$RefNighborClusterSilPlot
dev.off()

allSumSpecifix<-dplyr::bind_rows(DysbioCluster2Stats$SumSpecifics,
                      DysbioCluster3Stats$SumSpecifics,
                      DysbioCluster4Stats$SumSpecifics,
                      DysbioCluster5Stats$SumSpecifics,
                      DysbioCluster6Stats$SumSpecifics,
                      DysbioCluster7Stats$SumSpecifics,
                      DysbioCluster8Stats$SumSpecifics,
                      DysbioCluster9Stats$SumSpecifics,
                      DysbioCluster10Stats$SumSpecifics,
                      DysbioCluster11Stats$SumSpecifics,
                      DysbioCluster12Stats$SumSpecifics,
                      DysbioCluster13Stats$SumSpecifics,
                      DysbioCluster14Stats$SumSpecifics,
                      DysbioCluster15Stats$SumSpecifics,
                      DysbioCluster16Stats$SumSpecifics)

allSumSpecifix$Cluster<-as.factor(allSumSpecifix$Cluster)

allSumSpecifix %>% 
  filter(Scheme == "Clusters_2" | Scheme == "Clusters_11") %>%
  filter(metric != "size") %>% 
  ggplot(aes(x=Cluster, y=unit, fill=Scheme))+
  theme_bw(base_size = 18) +
      labs(tag = "b") +
  geom_bar(stat="identity", position=position_dodge())+
  facet_wrap(~metric, scale = "free_y")+
            scale_fill_discrete(palette = c("grey", "black"))+
  theme(legend.position="none",
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 12),
        axis.title.y = element_text(size = 16),
        axis.text.y = element_text(size = 12),
        legend.margin = margin(t = 0, b = 0, r = 0, l = 0))->SchemeStats




pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/DysbioSumSpecifics_082926.pdf", width = 13, height = 11)
SchemeStats
dev.off()

rm(Dysbio2, clusterWeightDysbioAdult2, weightClusterDysbioAdults2,
   Dysbio3,DysbioCluster3Stats,clusterWeightDysbioAdult3, weightClusterDysbioAdults3,
   Dysbio4,DysbioCluster4Stats,clusterWeightDysbioAdult4, weightClusterDysbioAdults4,
   Dysbio5,DysbioCluster5Stats,clusterWeightDysbioAdult5, weightClusterDysbioAdults5,
   Dysbio6,DysbioCluster6Stats,clusterWeightDysbioAdult6, weightClusterDysbioAdults6,
   Dysbio7,DysbioCluster7Stats,clusterWeightDysbioAdult7, weightClusterDysbioAdults7,
   Dysbio8,DysbioCluster8Stats,clusterWeightDysbioAdult8, weightClusterDysbioAdults8,
   Dysbio9,DysbioCluster9Stats,clusterWeightDysbioAdult9, weightClusterDysbioAdults9,
   Dysbio10,DysbioCluster10Stats,clusterWeightDysbioAdult10, weightClusterDysbioAdults10,
  Dysbio11,DysbioCluster11Stats,clusterWeightDysbioAdult11, weightClusterDysbioAdults11,
   Dysbio12,DysbioCluster12Stats,clusterWeightDysbioAdult12, weightClusterDysbioAdults12,
   Dysbio13,DysbioCluster13Stats,clusterWeightDysbioAdult13, weightClusterDysbioAdults13,
   Dysbio14,DysbioCluster14Stats,clusterWeightDysbioAdult14, weightClusterDysbioAdults14,
   Dysbio15,DysbioCluster15Stats,clusterWeightDysbioAdult15, weightClusterDysbioAdults15,
   Dysbio16,DysbioCluster16Stats,clusterWeightDysbioAdult16, weightClusterDysbioAdults16
)

print(DysbioSummaryTable)
print(SchemeStats)

DysbioSummaryTable %>% 
  mutate(across(where(is.numeric), round, digits = 2)) %>% 
  relocate(TotalAvgSW, .before = lowList)->SuppFig5SumTb

wrap_table(SuppFig5SumTb, panel = "body", space = "fixed") + SchemeStats ->SuppFig5Top
pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/SuppFig5Top_082926.pdf", width = 11, height = 8.5)
SuppFig5Top
dev.off()

```

After determining 11 is the lowest %
```{r}
weightClusterDysbioAdults11 <- pam(myWeightUnipreFMTDM,11, keep.diss = TRUE)
clusterWeightDysbioAdult11 <- pam(myWeightUnipreFMTDM,11, cluster.only = TRUE)
DysbioCluster11Stats<-ClusteringSummary(weightClusterDysbioAdults11, "Clusters_11",NA, NA, 0,0.03)#this one looks good


set.seed(91)
Viridiff <- viridis(555, option = "A") #choose a large number of hexcodes from a color pallette
DysbioColors <- sprintf("%s", sample(Viridiff, 12))
DysbioColors <- setNames(DysbioColors, labelVectorRedo)

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/Dysbio11ClusterSummaryToggle_082926.pdf", width = 13, height = 11)
DysbioCluster11Stats$SummaryPlot
DysbioCluster11Stats$ClusterSilPlot
DysbioCluster11Stats$RefClusterSilPlot
DysbioCluster11Stats$RefNeighborClusterSilPlot
DysbioCluster11Stats$redoneNeighborsSWPlot
dev.off()

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/2and11SilPlotOverlayed_082926.pdf", width = 13, height = 11)
DysbioCluster2Stats$SilhouetteTable %>%
  mutate(id = row_number()) %>% 
  ggplot(aes(x=id, y=sil_width))+
  ggtitle("Comparing SWs for 2 Clusters and Neighbor Clusters by Cluster") +
  geom_col(width = 1, fill = "grey")+
  geom_col(data = DysbioCluster11Stats$SilhouetteTable %>%
             arrange(cluster,desc(sil_width)) %>% 
  mutate(id = row_number()),width = 1, fill = "black", alpha =0.8)+
  geom_col(data = DysbioCluster11Stats$redoneNeighborsSWs %>%
             arrange(unNeighborClusters,desc(sil_width)) %>% 
  mutate(id = row_number()),width = 1, fill = "red", alpha =0.7)+
    theme_minimal() +
    theme(
    panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside") + 
    xlab("SimpleID")

DysbioCluster2Stats$SilhouetteTable %>%
  mutate(id = row_number()) %>% 
  ggplot(aes(x=id, y=sil_width))+
  ggtitle("Comparing SWs for 2 Clusters and Neighbor Clusters by Sample SW") +
  geom_col(width = 1, fill = "grey")+
  geom_col(data = DysbioCluster11Stats$SilhouetteTable %>%
             arrange(desc(sil_width)) %>% 
  mutate(id = row_number()),width = 1, fill = "black", alpha =0.8)+
  geom_col(data = DysbioCluster11Stats$redoneNeighborsSWs %>%
             arrange(desc(sil_width)) %>% 
  mutate(id = row_number()),width = 1, fill = "red", alpha =0.7)+
    theme_minimal() +
    theme(
    panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside") + 
    xlab("SimpleID")
dev.off()
```

```{r, fig.width=13, fig.height=5}
DysbioCluster11Stats$SilhouetteTable %>%
  group_by(cluster) %>%
  dplyr::summarise(mean = round(mean(sil_width), digits = 4), n = n()) %>% 
  mutate(label =paste(cluster, "(",n,")", ":", mean))->OrigAvgSil

OrigAvgSil %>% 
   pull(label, name = cluster)->labelOrig

DysbioCluster11Stats$redoneNeighborsSWs %>%
  group_by(unNeighborClusters) %>%
  dplyr::summarise(mean = round(mean(sil_width), digits = 4), n = n()) %>% 
  mutate(label =paste(unNeighborClusters, "(",n,")", ":", mean)) %>% 
  ungroup()->NeighborAvgSil

NeighborAvgSil %>% 
   pull(label, name = unNeighborClusters)->Neighborlabel

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/ComparingClusterSWs_082926.pdf", width = 13, height = 8)
DysbioCluster11Stats$SilhouetteTable %>%
  mutate(id = row_number()) %>% 
  ggplot(aes(fill= cluster, x=id, y=sil_width))+
  geom_col(color = "black", linewidth = 0.13, width = 2)+
  facet_grid(~cluster, switch = "x", scales = "free_x", space = "free_x") +
  discrete_scale(aesthetics = "fill",
               palette = function(x) c(DysbioColors),
               labels = labelOrig)+
    theme_bw(base_size = 18) +
  labs(x = "Samples in Clusters",
       y = "Silhouette Width",
       tag =  "c")+
            theme(legend.position = "right",
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 12),
                axis.title.x = element_text(size = 12),
                axis.text.x = element_blank(),
                axis.tick.x = element_blank(),
                axis.title.y = element_text(size = 12),
                axis.text.y = element_text(size = 10),
                legend.margin = margin(t = 0, b = 0, r = 0, l = 0),
                panel.spacing = unit(0, "lines"), 
                strip.background = element_blank(),
                strip.placement = "outside")+
      scale_y_continuous(limits = c(-0.5,0.6))+
DysbioCluster11Stats$redoneNeighborsSWs %>%
  group_by(unNeighborClusters) %>% 
  arrange(desc(sil_width)) %>% 
  mutate(id = row_number()) %>% 
  ggplot(aes(fill= unNeighborClusters, x=id, y=sil_width))+
  geom_col(color = "black", linewidth = 0.13, width = 2)+
  facet_grid(~unNeighborClusters, switch = "x", scales = "free_x", space = "free_x") +
  discrete_scale(aesthetics = "fill",
               palette = function(x) c(DysbioColors),
               labels = Neighborlabel)+
    theme_bw(base_size = 18) +
  labs(x = "Samples in Clusters",
       y = "Silhouette Width")+
            theme(legend.position = "right",
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 12),
                axis.title.x = element_text(size = 12),
                axis.text.x = element_blank(),
                axis.tick.x = element_blank(),
                axis.title.y = element_text(size = 12),
                axis.text.y = element_text(size = 10),
                legend.margin = margin(t = 0, b = 0, r = 0, l = 0),
                panel.spacing = unit(0, "lines"), 
                strip.background = element_blank(),
                strip.placement = "outside")+
      scale_y_continuous(limits = c(-0.5,0.6))->ComparingSW
ComparingSW
dev.off()


NeighborStats<- as.tibble(c(
AvgSW= DysbioCluster11Stats$SilhouetteTable%>% 
  dplyr::summarise(mean = mean(sil_width)),
NeighborAvgSW=DysbioCluster11Stats$NeighborClusterNewSW %>% 
  dplyr::summarise(mean = mean(sil_width)),
unNeighborAvgSW=DysbioCluster11Stats$redoneNeighborsSWs%>% 
  dplyr::summarise(mean = mean(sil_width)),
AvgCount = DysbioCluster11Stats$redoneNeighborsSWs %>% 
  group_by(unNeighborClusters) %>% 
  dplyr::summarise(count = n()) %>% 
    ungroup() %>% 
  filter(unNeighborClusters != "unClustered") %>% 
    dplyr::summarise(avgSize = mean(count)),
NeighborNoUnclustAvgSW=DysbioCluster11Stats$NeighborClusterNewSW %>% 
  filter(ReNeighborClusters != "unClustered") %>% 
  dplyr::summarise(mean = mean(sil_width)),
unNeighborNoUnclustAvgSW=DysbioCluster11Stats$redoneNeighborsSWs%>% 
  filter(unNeighborClusters != "unClustered") %>% 
  dplyr::summarise(mean = mean(sil_width))))
#write_tsv(NeighborStats, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/dysbio11AvgSWs_082926.tsv", quote = "none")
```

going to make a metadata file for Analysis with cluster 11
```{r}
data.table::transpose(bind_rows(clusterWeightDysbioAdult11, .id = 'row'),make.names = 'row', keep.names = 'SampleID') ->myWeightClustersDysbioAdult11
myWeightClustersDysbioAdult11 <- as_tibble(myWeightClustersDysbioAdult11)
colnames(myWeightClustersDysbioAdult11)[2] <- 'Weight11ClusterDysbio'

myWeightRedefClustersDysbio11 <- as_tibble(DysbioCluster11Stats$RedefinedClusters)
colnames(myWeightRedefClustersDysbio11)[2] <- 'ReRefNeighbor11ClusterDysbio'

myWeightNeighborClustersDysbio11 <- as_tibble(DysbioCluster11Stats$RedefinedNeighborClusters)
colnames(myWeightNeighborClustersDysbio11)[2] <- 'Neighbor11ClusterDysbio'

myWeightUnNeighborClustersDysbio11 <- as_tibble(DysbioCluster11Stats$redoneNeighborsSWs)
myWeightUnNeighborClustersDysbio11 %>% 
  select(SampleID,unNeighborClusters)->myWeightUnNeighborClustersDysbio11
 

myWeightClustersDysbioAdult11 %>%
  left_join(myWeightRedefClustersDysbio11) %>% 
  left_join(myWeightNeighborClustersDysbio11)%>% 
  left_join(myWeightUnNeighborClustersDysbio11)->DysbioClusters

DysbioClusters %>% 
  rowid_to_column(var = "ID") %>%
  mutate(SimpleID = paste0("D", ID)) %>% 
  select(-ID)-> DysbioClusters

write_tsv(DysbioClusters, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/11w5DysbioClusters_082926.tsv", quote = "none")

myMeta %>% 
  left_join(DysbioClusters)->FullFMTClusterMeta
write_tsv(FullFMTClusterMeta, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/ReClusters3999Dysbio_metaAnalysis_082926.tsv" , quote = "none")


fullerunWeightUniFullPcoa %>% 
  left_join(DysbioClusters)->unWeightUniPcoaRedefDysbio11
write_tsv(unWeightUniPcoaRedefDysbio11, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/unWeighted3999DysFMTClusters_082926.tsv", quote = "none")

DysbioClusters %>% 
  left_join(fullerunWeightUniFullPcoa)->onlyRedef11DysbioMeta
```

assessing the goodness of this process
```{r}
DysbioCluster11Stats$SilhouetteTable %>% 
  filter(sil_width < 0)->initialNeighbors
#57

DysbioCluster11Stats$NeighborClusterNewSW %>% 
  filter(sil_width < 0 & ReNeighborClusters != "unClustered")->finalUnClust
#28

DysbioCluster11Stats$lowClustered ->finalUnClust
#48

DysbioCluster11Stats$SilhouetteTable %>% 
  mutate(firstPlacement = case_when(
                            sil_width < NA & sil_width > NA ~ "unClustered",
                            sil_width < 0 ~  "neighbor",
                             TRUE ~ "originalCluster")) ->firstNeighborAssigns
#count the number of samples that get assigned to neighbor, originalCluster, and unClustered in first round
firstNeighborAssigns %>% 
  dplyr::count(firstPlacement)->numberPlacements
#57 neighbor, 248 originalClusters

#now the new silhouette widths are going to place an additional number of samples into unClustered
DysbioCluster11Stats$NeighborClusterNewSW %>% 
  mutate(secondPlacement = case_when(sil_width < 0.03 & ReNeighborClusters != "unClustered" ~ "unClustered",
                             TRUE ~ "unchanged"))->secondNeighborAssigns

#count the number of samples that get assigned to unClustered in second round and that number added to first neighbor "unClustered" count should equal lowClustered
secondNeighborAssigns %>% 
  dplyr::count(secondPlacement)->number2Placements
#257 unchanged, 48 new Unclustered
firstNeighborAssigns %>% 
  select(SampleID,firstPlacement)->firstPlaceIDs
secondNeighborAssigns %>% 
  select(SampleID,secondPlacement)->secondPlaceIDs

firstPlaceIDs %>% 
  left_join(secondPlaceIDs)->placementAssignments
```

```{r}
#going to add Weighted PCoA data to each subset
myWeightUniPcoaDysbio <-read_qza('~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/core-metrics_MetaAnalysis_preFMT-1004/weighted_unifrac_pcoa_results.qza')$data
#get axis info
WeightUniFullProp <- myWeightUniPcoaDysbio$ProportionExplained[1:4]

#unweighted full prepare axis labels 
WeightDys1_xaxis = paste0('PC1 (', round(WeightUniFullProp [1], 3) * 100, '%)')
WeightDys2_yaxis = paste0('PC2 (', round(WeightUniFullProp [2], 3) * 100, '%)')
WeightDys3_xaxis = paste0('PC3 (', round(WeightUniFullProp [3], 3) * 100, '%)')
WeightDys4_yaxis = paste0('PC4 (', round(WeightUniFullProp [4], 3) * 100, '%)')

#turn them into tibbles and stuff
myWeightUniPcoaDysbio <- as_tibble(myWeightUniPcoaDysbio$Vectors)

colnames(myWeightUniPcoaDysbio)[1] <- 'SampleID'
colnames(myWeightUniPcoaDysbio)[2] <- 'PC1Dys_Wt'
colnames(myWeightUniPcoaDysbio)[3] <- 'PC2Dys_Wt'
colnames(myWeightUniPcoaDysbio)[4] <- 'PC3Dys_Wt'
colnames(myWeightUniPcoaDysbio)[5] <- 'PC4Dys_Wt'

# reducing data if needed
myWeightUniPcoaDysbio %>% 
  select(SampleID,PC1Dys_Wt, PC2Dys_Wt, PC3Dys_Wt, PC4Dys_Wt) ->lessWeighted123PCoADys

rm(myWeightUniPcoaDysbio, WeightUniFullProp)


fullerunWeightUniFullPcoa %>% 
  left_join(lessWeighted123PCoADys) %>% 
  left_join(DysbioClusters, join_by(SampleID))->metaUnWtUniFullSubWtPcoa
```

```{r}
##
##Health Weight
myWeightUniPcoaHealth <-read_qza('~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/070825_FilteredDataset/Enterotyping/core-metrics_MetaAnalysis_donor-1004/weighted_unifrac_pcoa_results.qza')$data
#get axis info
WeightUniFullPropHlth <- myWeightUniPcoaHealth$ProportionExplained[1:3]

#unweighted full prepare axis labels 
WeightHlth1_xaxis = paste0('PC1 (', round(WeightUniFullPropHlth [1], 3) * 100, '%)')
WeightHlth2_yaxis = paste0('PC2 (', round(WeightUniFullPropHlth [2], 3) * 100, '%)')
WeightHlth3_xaxis = paste0('PC2 (', round(WeightUniFullPropHlth [3], 3) * 100, '%)')

#turn them into tibbles and stuff
myWeightUniPcoaHealth <- as_tibble(myWeightUniPcoaHealth$Vectors)

colnames(myWeightUniPcoaHealth)[1] <- 'SampleID'
colnames(myWeightUniPcoaHealth)[2] <- 'PC1Hlth_Wt'
colnames(myWeightUniPcoaHealth)[3] <- 'PC2Hlth_Wt'
colnames(myWeightUniPcoaHealth)[4] <- 'PC3Hlth_Wt'

# reducing data if needed
myWeightUniPcoaHealth %>% 
  select(SampleID,PC1Hlth_Wt, PC2Hlth_Wt, PC3Hlth_Wt) ->lessWeighted123PCoAHlth

rm(myWeightUniPcoaHealth, WeightUniFullPropHlth)

```


```{r, fig.width=18, fig.height=8}
#Dysbio
metaUnWtUniFullSubWtPcoa$Weight11ClusterDysbio <- as.character(metaUnWtUniFullSubWtPcoa$Weight11ClusterDysbio)
metaUnWtUniFullSubWtPcoa$ReRefNeighbor11ClusterDysbio <- as.character(metaUnWtUniFullSubWtPcoa$ReRefNeighbor11ClusterDysbio)
metaUnWtUniFullSubWtPcoa$un<- as.character(metaUnWtUniFullSubWtPcoa$unNeighborClusters)

metaUnWtUniFullSubWtPcoa %>% 
filter(unNeighborClusters != "NA") %>% 
  group_by(target_subfragment) %>%
dplyr::count(unNeighborClusters) ->inforedefinedSubFrag

labelVectorRedo <- setNames(c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, "unClustered"), c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "BTC"))

Viridiff <- viridis(555, option = "A")
set.seed(94)
PrimerColors <- sprintf("%s", sample(Viridiff, 6))
set.seed(91)
DysbioColors <- sprintf("%s", sample(Viridiff, 12))
DysbioColors <- setNames(DysbioColors, labelVectorRedo)
set.seed(99)
StudyColors <- sprintf("%s", sample(Viridiff, 14))
set.seed(94)
HealthColors <- sprintf("%s", sample(Viridiff, 7))

#dysbio
pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/subFragmentByNeighborClusterPlot_082926.pdf", width = 13, height = 11)
inforedefinedSubFrag  %>%   
  ggplot(aes(fill=target_subfragment, y= n, x= unNeighborClusters)) +
  theme_bw(base_size = 18) +
  labs(title = "Samples from Each of 11 Dysbio Clusters",
       subtitle = "By Subfragment",
       x = "Cluster",
       y = "Samples Count",
       tag = "a")+
  geom_bar(position="stack", stat="identity",color = "black", linewidth = 0.3,)+
          discrete_scale(aesthetics = "fill",
               palette = function(x) c(PrimerColors))+
        theme(legend.position = "bottom",
              plot.title = element_text( size = 14),
                plot.subtitle = element_text( size = 12),
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 12),
                axis.title.x = element_text(size = 12),
                axis.text.x = element_text(size = 10),
                axis.title.y = element_text(size = 12),
                axis.text.y = element_text(size = 10),
                legend.margin = margin(t = 0, b = 0, r = 0, l = 0))+
    scale_x_discrete(limits=c(1,2,3,4,5,6,7,8,9,10,11,"unClustered"),
                     labels=labelVectorRedo)->SubFragEffect
SubFragEffect
dev.off()

metaUnWtUniFullSubWtPcoa %>% 
filter(unNeighborClusters != "NA") ->DysbioreRefinedData
  
SubfragData<- table(DysbioreRefinedData$unNeighborClusters, DysbioreRefinedData$target_subfragment)
resultSub <- chisq.test(SubfragData)
print(resultSub)
#significant relationship (X-squared = 280.27, df = 55, p-value < 2.2e-16)              
resultSub$expected
cramResultSub<-cramerV(SubfragData)
print(cramResultSub)
#moderate effect size (0.4287)

metaUnWtUniFullSubWtPcoa %>% 
filter(unNeighborClusters != "NA") %>% 
  group_by(experiment_title) %>%
dplyr::count(unNeighborClusters) ->inforedefinedStudy


pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/studyByNeighborClusterPlot_082926.pdf", width = 13, height = 11)
inforedefinedStudy  %>%   
  ggplot(aes(fill=experiment_title, y= n, x= unNeighborClusters)) +
  theme_bw(base_size = 18) +
  labs(title = "Samples from Each of 11 Dysbio Clusters",
       subtitle = "By Study",
       x = "Cluster",
       y = "Samples Count",
       tag = "b")+
  geom_bar(position="stack", stat="identity",color = "black", linewidth = 0.3,)+
          discrete_scale(aesthetics = "fill",
               palette = function(x) c(StudyColors))+
        theme(legend.position = "bottom",
              plot.title = element_text( size = 14),
                plot.subtitle = element_text( size = 12),
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 12),
                axis.title.x = element_text(size = 12),
                axis.text.x = element_text(size = 10),
                axis.title.y = element_text(size = 12),
                axis.text.y = element_text(size = 10),
                legend.margin = margin(t = 0, b = 0, r = 0, l = 0))+
    scale_x_discrete(limits=c(1,2,3,4,5,6,7,8,9,10,11,"unClustered"),
                     labels=labelVectorRedo)->StudyEffect
StudyEffect
dev.off()


StudyData<- table(DysbioreRefinedData$unNeighborClusters, DysbioreRefinedData$experiment_title)
resultStudy <- chisq.test(StudyData, simulate.p.value = TRUE)
print(resultStudy)
#significant relationship (X-squared = 400.86, df = NA, p-value = 0.0004998)  
resultStudy$expected
cramResultStudy<-cramerV(StudyData)
print(cramResultStudy)
#moderate effect size (0.3457 )


SubFragEffect+StudyEffect->SuppFig6

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/SuppFig6_082926.pdf", width = 11, height = 8.5)
SuppFig6
dev.off()
```
adonis
```{r}
#dysbio
meta_ordered <- onlyRedef11DysbioMeta[match(rownames(as.matrix(myWeightUnipreFMTDM)), onlyRedef11DysbioMeta$SampleID), ]
#304 PreFMT samples
meta_ordered$experiment_title <- factor(meta_ordered$experiment_title)
meta_ordered$target_subfragment <- factor(meta_ordered$target_subfragment)
meta_ordered$unNeighborClusters <- factor(meta_ordered$unNeighborClusters)

#does cluster explain variation, what do others explain
adonic_result <- adonis2(
                        myWeightUnipreFMTDM ~ target_subfragment + experiment_title + unNeighborClusters,
                        data = meta_ordered,
                        permutations =  999,
                        by = "terms")
#does cluster explain variation after correcting for study
adonic_result2 <- adonis2(
                        myWeightUnipreFMTDM ~ experiment_title + target_subfragment + unNeighborClusters,
                        data = meta_ordered,
                        by = "margin")
DysbioAdonis<-rownames_to_column(adonic_result2, "variable")
#R2 went up to .42 from .38 after neighbors reassignment for Samples, but also putting the 3 samples in cluster 5 in unClustered
#R2 went up to .45 from .42 after neighbors reassignment for SW <0, keeping 5, and then assigning SW<0.03 to unclust
write_tsv(DysbioAdonis, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/Dysbio11NeighborClusterAdonis_082926.tsv", quote = "none")
```


```{r}
dysbioDist <- read_tsv('~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/MetaSampleDysbioDistances_083126.tsv')

#Attaching dysbio distances onto lotsa meta data
metaUnWtUniFullSubWtPcoa%>% 
  left_join(dysbioDist)->metaUnWtUniFullSubWtPcoaDD

metaUnWtUniFullSubWtPcoaDD %>% 
  filter(unNeighborClusters != 'NA') %>% 
    group_by(unNeighborClusters) %>% 
    summarise(medianDysDist = median(dysbiosis_dist), mean = mean(dysbiosis_dist), 
              minimum = min(dysbiosis_dist), maximum = max(dysbiosis_dist),
              IQR = IQR(dysbiosis_dist), sd = sd(dysbiosis_dist), n = n())-> Dys11DstanceAvgs

#write_tsv(Dys11DstanceAvgs, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/Dysbio11w5DistanceSumTab_083126.tsv", quote = "none")

#dysbio 11 redo
centersUnWt<- aggregate(cbind(PC1_UnWt, PC2_UnWt) ~ unNeighborClusters, data=metaUnWtUniFullSubWtPcoaDD, FUN=mean)
centersWt <- aggregate(cbind(PC2Dys_Wt,PC1Dys_Wt) ~ unNeighborClusters, data=metaUnWtUniFullSubWtPcoaDD, FUN=mean)
centersWt %>% 
  left_join(centersUnWt) %>% 
  left_join(Dys11DstanceAvgs)->CentersAvgTabel

colnames(CentersAvgTabel)[2] <- 'PC2Dys_WtAv'
colnames(CentersAvgTabel)[3] <- 'PC1Dys_WtAv'
colnames(CentersAvgTabel)[4] <- 'PC1Dys_UnWtAv'
colnames(CentersAvgTabel)[5] <- 'PC2Dys_UnWtAv'
```


```{r, fig.width=13, fig.height=7}
metaUnWtUniFullSubWtPcoa %>%
  left_join(placementAssignments) %>% 
   ggplot() +
    theme_bw(base_size = 18) +
    xlab(WeightDys1_xaxis) +
    ylab(WeightDys2_yaxis) +
  ggtitle("Weighted Meta-analysis Placement Assignments of Dysbiotic Enterotypes") +
    geom_point(data = metaUnWtUniFullSubWtPcoa %>% 
               filter(unNeighborClusters != "NA"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt,fill = unNeighborClusters),alpha = 0.4, pch = 21, size = 7) +
        discrete_scale(aesthetics = "fill",
               palette = function(x) c(DysbioColors),
                labels = labelVectorRedo)+
              new_scale_fill() +
    geom_point(data = . %>% 
               filter(unNeighborClusters != "NA"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt, fill = firstPlacement), pch = 21, size = 3) +
  scale_fill_discrete(palette = c("black","white"))+
    geom_point(data = . %>% 
               filter(secondPlacement == "unClustered"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt),pch = 21, fill = "red", size = 3)


metaUnWtUniFullSubWtPcoa %>%
  left_join(placementAssignments) %>% 
   ggplot() +
    theme_bw(base_size = 18) +
    xlab(WeightDys1_xaxis) +
    ylab(WeightDys2_yaxis) +
  ggtitle("Weighted Meta-analysis Placement Assignments of Dysbiotic Enterotypes") +
         geom_point(data = CentersAvgTabel %>%
                group_by(unNeighborClusters), 
                aes(y= PC2Dys_WtAv, x= PC1Dys_WtAv, fill=unNeighborClusters),
                    pch = 21, size = 15, alpha = 0.3)+
          discrete_scale(aesthetics = "fill",
               palette = function(x) c(DysbioColors),
                labels = labelVectorRedo)+
    geom_point(data = . %>% 
               filter(unNeighborClusters != "NA"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt, shape = firstPlacement, fill = unNeighborClusters), size = 3, alpha = 0.4) + 
    scale_shape_manual(values=c(25,21,8))+
    geom_point(data = . %>% 
               filter(secondPlacement == "unClustered"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt), color = "red", shape = 4, size = 3)

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/w5NeighborUnclustAssignments_083126.pdf", width = 13, height = 8.5)
metaUnWtUniFullSubWtPcoa %>%
   left_join(placementAssignments) %>% 
    ggplot() +
  labs(title = "Weighted Meta-analysis Placement Assignments",
       x = WeightDys1_xaxis,
       y = WeightDys2_yaxis,
       tag = "b")+
     theme_bw(base_size = 18) +
       geom_point(data = . %>% 
                filter(unNeighborClusters != "NA"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt, shape = firstPlacement), color = "black", stroke =0.3, size = 4.5)+ 
     geom_point(data = . %>% 
                filter(unNeighborClusters != "NA"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt, shape = firstPlacement, color = unNeighborClusters),stroke =1.25, size = 3) + 
         geom_point(data = . %>% 
                filter(unNeighborClusters != "NA"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt, shape = firstPlacement), color = "black",stroke =0.3,size = 2.5)+ 
    discrete_scale(aesthetics = "color",
          palette = function(x) c(DysbioColors),
          labels = labelVectorRedo)+
     scale_shape_manual(values=c(25,21,8))+
          theme(legend.position = "right",
              plot.title = element_text( size = 14),
                plot.subtitle = element_text( size = 12),
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 12),
                axis.title.x = element_text(size = 12),
                axis.text.x = element_text(size = 10),
                axis.title.y = element_text(size = 12),
                axis.text.y = element_text(size = 10),
                legend.margin = margin(t = 0, b = 0, r = 0, l = 0))+
     geom_point(data = . %>% 
                filter(secondPlacement == "unClustered"),
                aes(y= PC2Dys_Wt, x= PC1Dys_Wt), color = "red", shape = 4, size = 3)->PlacementFig
PlacementFig
dev.off()
```

```{r, fig.width=15, fig.height=12}

SuppFig5Top/PlacementFig/ComparingSW->SuppFig5

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/Supp_Fig5_072326.pdf", width = 15, height = 12)
SuppFig5
dev.off()
```
```{r}
weightClusterDysbioAdults11 <- pam(myWeightUnipreFMTDM,11, keep.diss = TRUE)
weightClusterDysbioAdults11$medoids->medoids11
```
Healthy things
clustering Healthy Adults
Keep note that Sample ID SRR1169808 from  Seekatz454 is labelled as both preFMT and healthy adult! And therefore is clustered for both health and dysbio. Check it out to find out what is up
```{r}
## load in weightUNI distance matrix
myWeightUniHealthAdultsDM <-read_qza('~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/070825_FilteredDataset/Enterotyping/core-metrics_MetaAnalysis_donor-1004/weighted_unifrac_distance_matrix.qza')$data

## Use the silhouette widths for assessing the best number of clusters,
## following a one-dimensional example from Christian Hennig :
## this is in the cluster PDF

#Partitioning (clustering) of the data into k clusters “around medoids”, a more robust version of K-means.
weightClusterHealthAdults2 <- pam(myWeightUniHealthAdultsDM,2, keep.diss = TRUE)
clusterWeightHealthAdult2 <- pam(myWeightUniHealthAdultsDM,2, cluster.only = TRUE)
weightClusterHealthAdults3 <- pam(myWeightUniHealthAdultsDM,3, keep.diss = TRUE)
clusterWeightHealthAdult3 <- pam(myWeightUniHealthAdultsDM,3, cluster.only = TRUE)
weightClusterHealthAdults4 <- pam(myWeightUniHealthAdultsDM,4, keep.diss = TRUE)
clusterWeightHealthAdult4 <- pam(myWeightUniHealthAdultsDM,4, cluster.only = TRUE)

weightClusterHealthAdults5 <- pam(myWeightUniHealthAdultsDM,5, keep.diss = TRUE)
clusterWeightHealthAdult5 <- pam(myWeightUniHealthAdultsDM,5, cluster.only = TRUE)
weightClusterHealthAdults6 <- pam(myWeightUniHealthAdultsDM,6, keep.diss = TRUE)
clusterWeightHealthAdult6 <- pam(myWeightUniHealthAdultsDM,6, cluster.only = TRUE)
weightClusterHealthAdults7 <- pam(myWeightUniHealthAdultsDM,7, keep.diss = TRUE)
clusterWeightHealthAdult7 <- pam(myWeightUniHealthAdultsDM,7, cluster.only = TRUE)

weightClusterHealthAdults8 <- pam(myWeightUniHealthAdultsDM,8, keep.diss = TRUE)
clusterWeightHealthAdult8 <- pam(myWeightUniHealthAdultsDM,8, cluster.only = TRUE)

HealthCluster2Stats<-ClusteringSummary(weightClusterHealthAdults2, "Clusters_2")
HealthCluster3Stats<-ClusteringSummary(weightClusterHealthAdults3, "Clusters_3")
HealthCluster4Stats<-ClusteringSummary(weightClusterHealthAdults4, "Clusters_4")
HealthCluster5Stats<-ClusteringSummary(weightClusterHealthAdults5, "Clusters_5")
HealthCluster6Stats<-ClusteringSummary(weightClusterHealthAdults6, "Clusters_6")
HealthCluster7Stats<-ClusteringSummary(weightClusterHealthAdults7, "Clusters_7")

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/070825_FilteredDataset/Enterotyping/HealthyClusterSummary_051126.pdf", width = 13, height = 11)
HealthCluster2Stats$SummaryPlot
HealthCluster3Stats$SummaryPlot
HealthCluster4Stats$SummaryPlot
HealthCluster7Stats$SummaryPlot
HealthCluster2Stats$ClusterSilPlot
HealthCluster3Stats$ClusterSilPlot
HealthCluster4Stats$ClusterSilPlot
HealthCluster7Stats$ClusterSilPlot
HealthCluster2Stats$RefClusterSilPlot
HealthCluster3Stats$RefClusterSilPlot
HealthCluster4Stats$RefClusterSilPlot
HealthCluster7Stats$RefClusterSilPlot
dev.off()

health2<-HealthCluster2Stats$DistanceSummary
health2$HealthClusters <- "2"
health3<-HealthCluster3Stats$DistanceSummary
health3$HealthClusters <- "3"
health4<-HealthCluster4Stats$DistanceSummary
health4$HealthClusters <- "4"

health5<-HealthCluster5Stats$DistanceSummary
health5$HealthClusters <- "5"
health6<-HealthCluster6Stats$DistanceSummary
health6$HealthClusters <- "6"
health7<-HealthCluster7Stats$DistanceSummary
health7$HealthClusters <- "7"

lowList<-c(HealthCluster2Stats$PercentLowClusters,
           HealthCluster3Stats$PercentLowClusters,
          HealthCluster4Stats$PercentLowClusters,
          HealthCluster5Stats$PercentLowClusters,
           HealthCluster6Stats$PercentLowClusters,
          HealthCluster7Stats$PercentLowClusters)

HealthClusters<-c("2","3","4","5","6","7")

lowTable<-tibble(HealthClusters,lowList)
health2 %>% 
  full_join(health3) %>% 
  full_join(health4)%>% 
  full_join(health5)%>% 
  full_join(health6)%>% 
  full_join(health7) ->healthStats

lowTable %>% 
  left_join(healthStats) ->HlthSummaryTable
#3 has the lower Percent (.33) of clusters with avg sil widths less than 0.1
#But also if you add cluster schemes 5,6,7 the percLow goes down consistently and seven seems best

#write_tsv(HlthSummaryTable, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/070825_FilteredDataset/Enterotyping/healthSummaryList_051126.tsv", quote = "none")

#choose clustering scheme with lowest percentage of clusters that have avg. silhouette width <0.1. Remove other files

rm(health2,HealthCluster2Stats, myWeightClustersHealthAdult2, weightClusterHealthAdults2,
   health5,HealthCluster5Stats, myWeightClustersHealthAdult5, weightClusterHealthAdults5,
   health6,HealthCluster6Stats, myWeightClustersHealthAdult6, weightClusterHealthAdults6)

#3
data.table::transpose(bind_rows(clusterWeightHealthAdult3, .id = 'row'),make.names = 'row', keep.names = 'SampleID') ->myWeightClustersHealthAdult3
myWeightClustersHealthAdult3 <- as_tibble(myWeightClustersHealthAdult3)
colnames(myWeightClustersHealthAdult3)[2] <- 'Weight3ClusterHealth'
#get Redefined Clusters
myWeightReClustersHealth3 <- as_tibble(HealthCluster3Stats$RedefinedClusters)
colnames(myWeightReClustersHealth3)[2] <- 'RedefWeight3ClusterHealth'
#4
data.table::transpose(bind_rows(clusterWeightHealthAdult4, .id = 'row'),make.names = 'row', keep.names = 'SampleID') ->myWeightClustersHealthAdult4
myWeightClustersHealthAdult4 <- as_tibble(myWeightClustersHealthAdult4)
colnames(myWeightClustersHealthAdult4)[2] <- 'Weight4ClusterHealth'
#get Redefined Clusters
myWeightReClustersHealth4 <- as_tibble(HealthCluster4Stats$RedefinedClusters)
colnames(myWeightReClustersHealth4)[2] <- 'RedefWeight4ClusterHealth'
#7
data.table::transpose(bind_rows(clusterWeightHealthAdult7, .id = 'row'),make.names = 'row', keep.names = 'SampleID') ->myWeightClustersHealthAdult7
myWeightClustersHealthAdult7 <- as_tibble(myWeightClustersHealthAdult7)
colnames(myWeightClustersHealthAdult7)[2] <- 'Weight7ClusterHealth'
#get Redefined Clusters
myWeightReClustersHealth7 <- as_tibble(HealthCluster7Stats$RedefinedClusters)
colnames(myWeightReClustersHealth7)[2] <- 'RedefWeight7ClusterHealth'

myWeightClustersHealthAdult3 %>% 
  left_join(myWeightClustersHealthAdult7)%>% 
  left_join(myWeightClustersHealthAdult4)%>% 
  left_join(myWeightReClustersHealth3)%>% 
  left_join(myWeightReClustersHealth7)%>% 
  left_join(myWeightReClustersHealth4)->EubioTable

EubioTable %>% 
  rowid_to_column(var = "ID") %>%
  mutate(SimpleID = paste0("H", ID)) %>% 
  select(-ID)-> EubioTable

EubioTable %>% 
    left_join(fullerunWeightUniFullPcoa)->onlyHealthyEnterosMeta
  
fullerunWeightUniFullPcoa %>% 
  left_join(EubioTable) ->unWeightUniPcoaRedefHealth
#write_tsv(unWeightUniPcoaRedefHealth, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/070825_FilteredDataset/Enterotyping/unWeighted3999HlthFMTClusters_051126.tsv", quote = "none")

```
Healthy clustering has been a bit confusing - wondering if subsetting further by variable region might help reduce cluster number
Keith has done this previously and this is his code 
Create two groups for analysis. The V1-4 group and the V5-7 group as they separate nicely on the PCoA plot
```{r}
# #create character vectors of V1-4 group and V5-7 group
# high <- c("V5-V7", "V6", "V5-V6", "V3-V5")
# low <- c("V3-V4","V1-V3","V4","V2","V3")
# 
# #create tibbles of high and low groups
# plot_high <- test %>% filter(exp_type == "FMT" & fmt_status %in% c("donor", "PostFMT", "PreFMT") & target_subfragment %in% high)
# plot_low <- test %>% filter(exp_type == "FMT" & fmt_status %in% c("donor", "PostFMT", "PreFMT") & target_subfragment %in% low)
# 
# #re-leveling factors to fix colors below
# plot_high <- plot_high %>% mutate(fmt_status = fct_relevel(fmt_status, "donor", "PostFMT", "PreFMT"))
# plot_low <- plot_low %>% mutate(fmt_status = fct_relevel(fmt_status, "donor", "PostFMT", "PreFMT"))

```
is this clustering a batch effect, host_subject_id effect, study effect?
```{r}
# metaUnWtUniFullSubWtPcoa$RedefWeight3ClusterHealth<- as.character(metaUnWtUniFullSubWtPcoa$RedefWeight3ClusterHealth)
# metaUnWtUniFullSubWtPcoa$Weight3ClusterHealth<- as.character(metaUnWtUniFullSubWtPcoa$Weight3ClusterHealth)
# metaUnWtUniFullSubWtPcoa$Weight4ClusterHealth <- as.character(metaUnWtUniFullSubWtPcoa$Weight4ClusterHealth)
# metaUnWtUniFullSubWtPcoa$Weight7ClusterHealth <- as.character(metaUnWtUniFullSubWtPcoa$Weight7ClusterHealth)
# metaUnWtUniFullSubWtPcoa$RedefWeight7ClusterHealth<- as.character(metaUnWtUniFullSubWtPcoa$RedefWeight7ClusterHealth)
# metaUnWtUniFullSubWtPcoa$RedefWeight4ClusterHealth<- as.character(metaUnWtUniFullSubWtPcoa$RedefWeight4ClusterHealth)
# #newEub
# metaUnWtUniFullSubWtPcoa$Weight2ClusterHealth<- as.character(metaUnWtUniFullSubWtPcoa$Weight2ClusterHealth)
# metaUnWtUniFullSubWtPcoa$unNeighborWeight2ClusterHealth<- as.character(metaUnWtUniFullSubWtPcoa$unNeighborWeight2ClusterHealth)
# 
# metaUnWtUniFullSubWtPcoa$unNeighborH2Hazleton <- as.character(metaUnWtUniFullSubWtPcoa$unNeighborH2Hazleton)
# 
# metaUnWtUniFullSubWtPcoa$unNeighborH2KhannaK <- as.character(metaUnWtUniFullSubWtPcoa$unNeighborH2KhannaK)
# 
# metaUnWtUniFullSubWtPcoa$unNeighborH3Fricke<- as.character(metaUnWtUniFullSubWtPcoa$unNeighborH3Fricke)
```

```{r}
#Healthy

metaUnWtUniFullSubWtPcoa %>% 
filter(RedefWeight7ClusterHealth != "NA") %>% 
  group_by(target_subfragment) %>% 
dplyr::count(RedefWeight7ClusterHealth) ->inforedefinedSubFrag7

labelVectorRedo7 <- setNames(c(2, 3, 4, 6, 7, 'unClustered'), c("2", "3", "4", "6", "7","unClustered"))

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/070825_FilteredDataset/Enterotyping/subFragmentByClusterPlotH7redo.pdf", width = 13, height = 11)
inforedefinedSubFrag7  %>%   
  ggplot(aes(fill=target_subfragment, y= n, x= RedefWeight7ClusterHealth)) +
      ggtitle("Samples from each of 7 redo Healthy clusters by SubFrag") +
    geom_bar(position="stack", stat="identity")+
          discrete_scale(aesthetics = "fill",
               palette = function(x) c(HealthColors))+
    scale_x_discrete(limits=c(2,3,4,5,6,7,"unClustered"),
                     labels=labelVectorRedo7)


metaUnWtUniFullSubWtPcoa %>% 
filter(RedefWeight7ClusterHealth != "NA") ->HlthreRefinedData
  
SubfragData<- table(HlthreRefinedData$RedefWeight7ClusterHealth, HlthreRefinedData$target_subfragment)
resultSub <- chisq.test(SubfragData)
print(resultSub)
#3 Clusters has significant relationship (X-squared = 348, df = 10, p-value <2e-16) 
#7 Clusters has significant relationship (X-squared = 704, df = 30, p-value <2e-16)
#7redo Clusters has significant relationship (X-squared = 478, df = 30, p-value <2e-16)  
resultSub$expected
cramResultSub<-cramerV(SubfragData)
print(cramResultSub)
#3 Clusters moderate effect size (0.56)
#7 Clusters moderate effect size (0.5)
#7redo Clusters moderate effect size (0.41)

metaUnWtUniFullSubWtPcoa %>% 
filter(RedefWeight7ClusterHealth != "NA") %>% 
  group_by(experiment_title) %>%
dplyr::count(RedefWeight7ClusterHealth) ->inforedefinedStudy7


pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/070825_FilteredDataset/Enterotyping/studyByClusterPlotH7redo.pdf", width = 13, height = 11)
inforedefinedStudy7  %>%   
  ggplot(aes(fill=experiment_title, y= n, x= RedefWeight7ClusterHealth)) +
    ggtitle("Samples from each of 7 redo Healthy clusters by Study") +
    geom_bar(position="stack", stat="identity")+
          discrete_scale(aesthetics = "fill",
               palette = function(x) c(StudyColors))+
    scale_x_discrete(limits=c(2,3,4,5,6,7, "unClustered"),
                     labels=labelVectorRedo7)
dev.off()
```

```{r}
#healthy
meta_orderedH2 <- onlyHealthyEnterosMeta[match(rownames(as.matrix(myWeightUniHealthAdultsDM)), onlyHealthyEnterosMeta$SampleID), ]
#549 donor samples
meta_orderedH2$experiment_title <- factor(meta_orderedH2$experiment_title)
meta_orderedH2$target_subfragment <- factor(meta_orderedH2$target_subfragment)
meta_orderedH2$unNeighborWeight2ClusterHealth <- factor(meta_orderedH2$unNeighborWeight2ClusterHealth)

adonic_resultH2 <- adonis2(
                        myWeightUniHealthAdultsDM ~ experiment_title + target_subfragment + unNeighborWeight2ClusterHealth,
                        data = meta_orderedH2,
                        by = "margin")
H2Adonis<-rownames_to_column(adonic_resultH2, "variable")
write_tsv(H2Adonis, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/070825_FilteredDataset/Enterotyping/Health3ClusterAdonis_070626.tsv", quote = "none")

meta_orderedH4 <- onlyHealthyEnterosMeta[match(rownames(as.matrix(myWeightUniHealthAdultsDM)), onlyHealthyEnterosMeta$SampleID), ]
#556 donor samples
meta_orderedH4$experiment_title <- factor(meta_orderedH4$experiment_title)
meta_orderedH4$target_subfragment <- factor(meta_orderedH4$target_subfragment)
meta_orderedH4$RedefWeight4ClusterHealth <- factor(meta_orderedH4$RedefWeight4ClusterHealth)

adonic_result2H4 <- adonis2(
                        myWeightUniHealthAdultsDM ~ experiment_title + target_subfragment + RedefWeight4ClusterHealth,
                        data = meta_orderedH4,
                        by = "margin")
H4Adonis<-rownames_to_column(adonic_result2H4, "variable")
write_tsv(H4Adonis, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/070825_FilteredDataset/Enterotyping/Health4redoClusterAdonis_051126.tsv", quote = "none")

##Adonis H7
meta_orderedH7 <- onlyHealthyEnterosMeta[match(rownames(as.matrix(myWeightUniHealthAdultsDM)), onlyHealthyEnterosMeta$SampleID), ]
#556 donor samples
meta_orderedH7$experiment_title <- factor(meta_orderedH7$experiment_title)
meta_orderedH7$target_subfragment <- factor(meta_orderedH7$target_subfragment)
meta_orderedH7$Weight7ClusterHealth <- factor(meta_orderedH7$Weight7ClusterHealth)

adonic_result2H7 <- adonis2(
                        myWeightUniHealthAdultsDM ~ experiment_title + target_subfragment + Weight7ClusterHealth,
                        data = meta_orderedH7,
                        by = "margin")
H7Adonis<-rownames_to_column(adonic_result2H7, "variable")
write_tsv(H7Adonis, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/070825_FilteredDataset/Enterotyping/HealtH7ClusterAdonis_051126.tsv", quote = "none")
#best so far with 0.18 R2

##Adonis H7redo
meta_orderedH7redo <- onlyHealthyEnterosMeta[match(rownames(as.matrix(myWeightUniHealthAdultsDM)), onlyHealthyEnterosMeta$SampleID), ]
#556 donor samples
meta_orderedH7redo$experiment_title <- factor(meta_orderedH7redo$experiment_title)
meta_orderedH7redo$target_subfragment <- factor(meta_orderedH7redo$target_subfragment)
meta_orderedH7redo$RedefWeight7ClusterHealth <- factor(meta_orderedH7redo$RedefWeight7ClusterHealth)

adonic_result2H7redo <- adonis2(
                        myWeightUniHealthAdultsDM ~ experiment_title + target_subfragment + RedefWeight7ClusterHealth,
                        data = meta_orderedH7redo,
                        by = "margin")
H7redoAdonis<-rownames_to_column(adonic_result2H7redo, "variable")
write_tsv(H7redoAdonis, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/070825_FilteredDataset/Enterotyping/HealtH7redoClusterAdonis_051126.tsv", quote = "none")
#0.16 R2
```

```{r}
fullEubioTable %>% 
  select(-SimpleID)->fullEubioTable
myMeta %>%  
  left_join(DysbioClusters, join_by(SampleID)) %>% 
  left_join(EubioTable, join_by(SampleID)) %>% 
  left_join(fullEubioTable, join_by(SampleID)) %>% 
  left_join(HazletonEubioTable, join_by(SampleID))%>% 
  left_join(KhannaKEubioTable, join_by(SampleID))%>% 
  left_join(frickeEubioTable, join_by(SampleID))->FullFMTClusterMeta1

FullFMTClusterMeta1%>%
  mutate(SimpleID = coalesce(SimpleID.x, SimpleID.y)) %>% 
  select(-SimpleID.x, - SimpleID.y)->FullFMTClusterMeta

#write_tsv(FullFMTClusterMeta1, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/070825_FilteredDataset/Enterotyping/ReClusters3999_metaAnalysis_070626.tsv", quote = "none")

#Just processing dysbio
myMeta %>%  
  left_join(DysbioClusters, join_by(SampleID))  ->DysbioFMTClusterMeta
#write_tsv(DysbioFMTClusterMeta, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/070825_FilteredDataset/Enterotyping/neighborDysCluster3999_metaAnalysis_063026.tsv", quote = "none")

```