---
title: "Meta-Determining Clusters"
author: "Elena Wall"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r, echo=FALSE}
#cleaning/functioning
library(broom)
library(tidyverse)
library(dplyr)
library(purrr)
library(speedyseq)

#analysis
library(NbClust)
library(Silhouette)
library(proxy)
library(qiime2R)
library(cluster)

#plotting
library(ggsignif)
library(cowplot)
library(ggplot2)
library(patchwork)
library(ggpubr)
library(ggpmisc)
library(ggforce)
library(ggnewscale)
library(gt)

#stats
library(rstatix)
library(rcompanion)
library(vegan)

#colors
library(RColorBrewer)
library(viridis)
library(farver)
library(grateful)

#cite_packages(output = "paragraph", out.dir = "~/Desktop/Lozupone_022425/Keith/Metaanalysis/")
```

```{r}
myMeta <- read_tsv('~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/metaMappingEW_KZHFiltered4.tsv')

myMeta <- as_tibble(myMeta)
colnames(myMeta)[1]<-"SampleID"

```
Going back to using metadata categories for enterotyping, so will need to use the subsetted core-diversity metrics from the 
```{r}
##
## Unweighted All
myUnweightUniFullPcoa <-read_qza('~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/core-metrics-OriginalMeta2-caseyFiltered-rared-1004/unweighted_unifrac_pcoa_results.qza')$data
#get axis info
unweightUniFullProp <- myUnweightUniFullPcoa$ProportionExplained[1:4]

#unweighted full prepare axis labels 
unweighted1_xaxis = paste0('PC1 (', round(unweightUniFullProp[1], 3) * 100, '%)')
unweighted2_yaxis = paste0('PC2 (', round(unweightUniFullProp[2], 3) * 100, '%)')
unweighted3_yaxis = paste0('PC3 (', round(unweightUniFullProp[3], 3) * 100, '%)')
unweighted4_yaxis = paste0('PC4 (', round(unweightUniFullProp[4], 3) * 100, '%)')

#turn them into tibbles and stuff
myUnweightUniFullPcoa <- as_tibble(myUnweightUniFullPcoa$Vectors)

colnames(myUnweightUniFullPcoa)[1] <- 'SampleID'
colnames(myUnweightUniFullPcoa)[2] <- 'PC1_UnWt'
colnames(myUnweightUniFullPcoa)[3] <- 'PC2_UnWt'
colnames(myUnweightUniFullPcoa)[4] <- 'PC3_UnWt'
colnames(myUnweightUniFullPcoa)[5] <- 'PC4_UnWt'

# reducing data if needed
myUnweightUniFullPcoa %>% 
  select(SampleID,PC1_UnWt, PC2_UnWt, PC3_UnWt, PC4_UnWt) ->lessUnweightedPCoA

rm(myUnweightUniFullPcoa, unweightUniFullProp)

myMeta %>% 
  left_join(lessUnweightedPCoA) ->fullerunWeightUniFullPcoa
#write_tsv(fullerunWeightUniFullPcoa, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/  unweightedPC123withMeta.tsv", quote = "none")
```
##Clustering
use metrics of each clusters fit to set threshold for "well clustered" samples
within PAM object is a clusinfo data table that can tell max and avg dissimilarity between the observations in the cluster and the cluster's medoid
also may be useful to use diameter of the cluster (maximal dissimilarity between two observations of the cluster)
```{r}
#provide a cluster object 
#a string of the cluster number that was used to create cluster object ("Clusters_11"), 
#silhouette maximum and minimum for 1st reassignment to unclustered (this was made for parameter testing and is not used in published work), 
#neighbor_thresh: threshold at which during first assignment observations are assingned to their neighbor cluster (eg. 0)
#unclust_thresh: threshold  at which during 2nd assignment observations are assingned to the BTC (eg. 0.03)
ClusteringSummary <-function(weightClusterNum, ClusterNumString, sil_max, sil_min, neighbor_thresh,unclust_thresh) 
  {
#obtain info from the pam clustering, get descriptive stats, and turn into usable form for plots and tables 
weightClusterNum$clusinfo->dis
dis %>% 
  as.tibble() ->dis

dis %>% 
  dplyr::summarise(across(where(is.numeric), mean, na.rm = TRUE)) %>% 
  round(., digits = 4)->sum
#transform
t(sum)->txSum
txSum<-as_tibble(txSum, rownames = "metric")
txSum %>% 
  filter(metric != "Cluster")->txSum
colnames(txSum)[2] <- 'mean'
txSum$mean <- as.character(txSum$mean)

#cleaning and tidying table
dis$Cluster <- rownames(dis)
dis$Scheme <- ClusterNumString
dis$Cluster <-as.numeric(dis$Cluster)
dis %>%
  as.tibble() %>% 
  gather(-Scheme, -Cluster, key=metric, value = unit)->tidyDiss

#make labels for plots
dis %>% 
   pull(Cluster, name = Cluster)->labelVector

#extract SW info for all observations
weightClusterNum$silinfo$widths->AllSilWidths
AllSilWidths %>% 
  as.tibble() ->AllSilWidths

#extract avg. SW info for dataset
weightClusterNum$silinfo$avg.width->AvgSilWidth

#giving summary table AvgSW
sum %>% 
    mutate(TotalAvgSW = AvgSilWidth)->sum
#this plots out the PAM objects specific metrics
tidyDiss %>% 
  ggplot()+
  geom_point(aes(x=Cluster, y=unit))+
  scale_x_discrete(limits=labelVector)+
  facet_wrap(~metric, scale = 'free_y',labeller = as_labeller(c(
  'av_diss' = "avg. dissimilarity from medoid",
  'diameter'= "diameter of cluster",
  'max_diss' ="max. dissimilarity from medoid",
  'separation' = "min. seperation of two cluster observations",
  'size' = "number of observations")))+
  geom_text(data = txSum, aes(x = Inf, y = Inf,
                              hjust = 1, vjust = 1,
                              label = mean))+
  ggtitle(ClusterNumString)->SummaryPlot

#this averages the SWs across samples in a cluster and determines if that cluster has avgSW <0.1 and provides a new label for plots that gives descriptive stats
AllSilWidths %>%
  group_by(cluster) %>%
  dplyr::summarise(mean = mean(sil_width), n = n()) %>% 
  mutate(isLow = mean < 0.1) %>% 
  mutate(label =paste(cluster, "(",n,")", ":", mean))->OrigAvgSil
 
#this will give the original clustering's % of clusters <0.1 for an output
percentLow <- (sum(OrigAvgSil$isLow))/(max(row_number(OrigAvgSil)))

#getting vector for labels
OrigAvgSil %>% 
   pull(label, name = cluster)->labelOrig

#order SWs
weightClusterNum$silinfo$widths->AllSilWidths
AllSilWidths<-as_tibble(AllSilWidths, rownames = "SampleID")
AllSilWidths$cluster <- as.factor(AllSilWidths$cluster)
AllSilWidths %>% 
  arrange(cluster,sil_width)->OrderedSilWidths

#silhouette plots of each cluster
OrderedSilWidths %>% 
  mutate(id = row_number()) %>% 
  ggplot(aes(fill = cluster, x=id, y=sil_width))+
  geom_col(width = 1)+
    facet_grid(~cluster, switch = "x", scales = "free_x", space = "free_x") +
    scale_fill_discrete(labels = labelOrig)+
    theme_minimal() +
    theme(axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside") + 
    xlab("Cluster")+
  ggtitle(ClusterNumString)->ClusterSil

##make a refined Cluster assignment before assigning to neighbors, this was iteration of clustering process and is now not used, but worth having the info
#saying everything with SW below 0.1 should go to unclustered, everyhting else stays as is
OrderedSilWidths %>% 
  mutate(RefinedClusters = case_when(sil_width < 0.10 ~ "12",
                             TRUE ~ cluster)) ->RefinedOrdSilWidths
#new cluster table
RefinedOrdSilWidths %>% 
  select(SampleID,RefinedClusters) ->ReDefinedClusters

#we need the correct order of the matrix to perform new SW calculations, this just ensures that
matchedRedefinedClusters <- ReDefinedClusters[match(rownames(as.matrix(weightClusterNum$diss)), ReDefinedClusters$SampleID), ]

#originally cluster 5 was 3 samples and was put into unclustered
#also not used anymore 
matchedRedefinedClusters %>% 
  mutate(RefinedClusters = case_when(RefinedClusters == "5" ~ "12", 
                             TRUE ~ RefinedClusters)) %>%  
 
#formatting for silhouette
    pull(RefinedClusters, name = SampleID) ->namedReAssignmentVector 
namedReAssignmentVector %>%
  as.integer()->reAssignmentVector
#recalculating SWs
reClusterSil<- silhouette(reAssignmentVector, weightClusterNum$diss)
rownames(reClusterSil)<-names(namedReAssignmentVector )
#making table of new SWs
reClusterSil %>% 
  as_tibble(rownames = "SampleID")->reClusterSWTable
colnames(reClusterSWTable)[2] <- 'RefinedClusters'

reClusterSWTable$RefinedClusters <- as.factor(reClusterSWTable$RefinedClusters)
reClusterSWTable %>% 
    mutate(RefinedClusters = case_when(RefinedClusters == "12" ~ "unClustered",
                             TRUE ~ RefinedClusters))->reClusterSWTable
#adding unclustered to labels
levelVector <- c(labelVector, "unClustered")

reClusterSWTable$RefinedClusters<- factor(reClusterSWTable$RefinedClusters, levels = c(levelVector))

reClusterSWTable %>% 
  arrange(RefinedClusters,sil_width) ->OrdRefSilWidths

#this averages the SWs across samples in a cluster and provides a new label for plots that gives descriptive stats
OrdRefSilWidths %>%
  group_by(RefinedClusters) %>%
  dplyr::summarise(mean = mean(sil_width), n = n()) %>% 
  mutate(label =paste(RefinedClusters, "(",n,")", ":", mean))->RefinedAvgSil

RefinedAvgSil %>% 
   pull(label, name = RefinedClusters)->labelRefined
# new SW plot
OrdRefSilWidths %>% 
  mutate(id = row_number()) %>% 
  ggplot(aes(fill = RefinedClusters, x=id, y=sil_width))+
  geom_col(width = 1)+
    facet_grid(~RefinedClusters, switch = "x", scales = "free_x", space = "free_x") +
    scale_fill_discrete(labels = labelRefined)+
    theme_minimal() +
    theme(axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside") + 
    xlab("RefinedClusters")+
  ggtitle(ClusterNumString)->RefClusterSil

#these will be outputs
OrdRefSilWidths %>% 
  select(SampleID,RefinedClusters) ->ReRefinedClusters

OrdRefSilWidths %>% 
  filter(RefinedClusters == "unClustered") %>% 
  select(SampleID)->unClusteredSamples

##make a Neighbor Clustering command that uses function inputs
AllSilWidths$neighbor <-as.character(AllSilWidths$neighbor)
AllSilWidths %>% 
  mutate(ReNeighborClusters = case_when(
                            sil_width < sil_max & sil_width > sil_min ~ "12",
                            sil_width < neighbor_thresh ~  neighbor,
                             TRUE ~ cluster)) ->RefinedNeighborSilWidths
#new table of redefined clusters
RefinedNeighborSilWidths %>% 
  select(SampleID,ReNeighborClusters) ->ReDefNeighborClusters

#as before, need to format correctly for matrix to be used in recalculated SW
matchedNeighborClusters <- ReDefNeighborClusters[match(rownames(as.matrix(weightClusterNum$diss)), ReDefNeighborClusters$SampleID), ]

#this is a remnant of not having cluster 5
matchedNeighborClusters %>% 
  mutate(ReNeighborClusters = case_when(#ReNeighborClusters == "5" ~ "12",
                             TRUE ~ ReNeighborClusters)) %>%  
   pull(ReNeighborClusters, name = SampleID) ->neighmedAssignmentVector 
neighmedAssignmentVector  %>%
  as.integer()->AssignmentVector

#recalculate SW
NeighborSil<- silhouette(AssignmentVector, weightClusterNum$diss)
rownames(NeighborSil)<-names(neighmedAssignmentVector )

#getting reassignment info for table and outputs, as above
NeighborSil %>% 
  as_tibble(rownames = "SampleID")->NeighborSWTable
colnames(NeighborSWTable)[2] <- 'ReNeighborClusters'

NeighborSWTable$ReNeighborClusters <- as.factor(NeighborSWTable$ReNeighborClusters)
NeighborSWTable %>% 
    mutate(ReNeighborClusters = case_when(ReNeighborClusters == "12" ~ "unClustered",
                             TRUE ~ ReNeighborClusters))->NeighborSWTable
NeighborSWTable$ReNeighborClusters <- factor(NeighborSWTable$ReNeighborClusters, levels = c(levelVector))
NeighborSWTable %>% 
  arrange(ReNeighborClusters,sil_width) ->OrdNeighborNewSWs

#see above for original and refined clusters
OrdNeighborNewSWs %>%
  group_by(ReNeighborClusters) %>%
  dplyr::summarise(mean = mean(sil_width), n = n()) %>% 
  mutate(label =paste(ReNeighborClusters, "(",n,")", ":", mean)) %>% 
  ungroup()->NeighborAvgSil

NeighborAvgSil %>% 
   pull(label, name = ReNeighborClusters)->labelNewNeigh

#make that plot
OrdNeighborNewSWs %>% 
  mutate(id = row_number()) %>% 
  ggplot(aes(fill = ReNeighborClusters, x=id, y=sil_width))+
  geom_col(width = 1)+
    facet_grid(~ReNeighborClusters, switch = "x", scales = "free_x", space = "free_x") +
    scale_fill_discrete(labels = labelNewNeigh)+
    theme_minimal() +
    theme(axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside") + 
    xlab("ReNeighborClusters")+
  ggtitle(ClusterNumString)->newNeighborSilPlot

##make poor Neighbors into unclustered
OrdNeighborNewSWs$neighbor <-as.character(OrdNeighborNewSWs$neighbor)
OrdNeighborNewSWs %>% 
  mutate(unNeighborClusters = case_when(sil_width < unclust_thresh & ReNeighborClusters != "unClustered" ~"12",
                                         ReNeighborClusters == "unClustered" ~ "12",
                             TRUE ~ ReNeighborClusters)) ->unNeighborSilWidths

unNeighborSilWidths %>% 
  select(SampleID,unNeighborClusters) ->unClustNeighborClusters

#formatting
matchedUnNeighborClusters <- unClustNeighborClusters[match(rownames(as.matrix(weightClusterNum$diss)), unClustNeighborClusters$SampleID), ]

matchedUnNeighborClusters %>% 
   pull(unNeighborClusters, name = SampleID) ->unNeighmedAssignmentVector 
unNeighmedAssignmentVector  %>%
  as.integer()->unNeighborAssignmentVector

#recalculate the SWs again
unNeighborSil<- silhouette(unNeighborAssignmentVector, weightClusterNum$diss)
rownames(unNeighborSil)<-names(unNeighmedAssignmentVector)

unNeighborSil %>% 
  as_tibble(rownames = "SampleID")->unNeighborSWTable
colnames(unNeighborSWTable)[2] <- 'unNeighborClusters'

unNeighborSWTable$unNeighborClusters <- as.factor(unNeighborSWTable$unNeighborClusters)
unNeighborSWTable %>% 
    mutate(unNeighborClusters = case_when(unNeighborClusters == "12" ~ "unClustered",
                             TRUE ~ unNeighborClusters))->unNeighborSWTable
unNeighborSWTable$unNeighborClusters <- factor(unNeighborSWTable$unNeighborClusters, levels = c(levelVector))
unNeighborSWTable %>% 
  arrange(unNeighborClusters,sil_width) ->OrdUnNeighborNewSWs

OrdUnNeighborNewSWs %>%
  group_by(unNeighborClusters) %>%
  dplyr::summarise(mean = mean(sil_width), n = n()) %>% 
  mutate(label =paste(unNeighborClusters, "(",n,")", ":", mean)) %>% 
  ungroup()->unNeighborAvgSil

unNeighborAvgSil %>% 
   pull(label, name = unNeighborClusters)->labelUnNeigh
#plot
OrdUnNeighborNewSWs %>% 
  mutate(id = row_number()) %>% 
  ggplot(aes(fill = unNeighborClusters, x=id, y=sil_width))+
  geom_col(width = 1)+
    facet_grid(~unNeighborClusters, switch = "x", scales = "free_x", space = "free_x") +
    scale_fill_discrete(labels = labelUnNeigh)+
    theme_minimal() +
    theme(axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside") + 
    xlab("redone Neighbor Clusters")+
  ggtitle(ClusterNumString)->unNeighborSilPlot

OrdUnNeighborNewSWs %>% 
  filter(unNeighborClusters == "unClustered") %>% 
  select(SampleID)->lowClusteredSamples

  return(list(SummaryPlot=SummaryPlot,
              SilhouetteTable=AllSilWidths,
              AverageSilWidth=OrigAvgSil,
              DistanceSummary = sum ,
              SumSpecifics = tidyDiss,
              PercentLowClusters = percentLow,
              ClusterSilPlot=ClusterSil,
              RefinedClustersSil = OrdRefSilWidths,
              RefClusterSilPlot=RefClusterSil,
              RefAvgSilWidths=RefinedAvgSil,
              RedefinedClusters = ReRefinedClusters,
              NeighborClusterNewSW = OrdNeighborNewSWs,
              RefNeighborClusterSilPlot=newNeighborSilPlot,
              RefAvgNeighborSW=NeighborAvgSil,
              RedefinedNeighborClusters = ReDefNeighborClusters,
              newSampleList = unClusteredSamples,
              redoneNeighborsSWs = OrdUnNeighborNewSWs,
              redoneNeighborsSWPlot = unNeighborSilPlot,
              redoneNeighborAvgSW=unNeighborAvgSil,
              lowClustered = lowClusteredSamples))
}
```

Dysbio Clustering to find the cluster scheme
```{r}
## load in weightUNI dysbio distance matrix
myWeightUnipreFMTDM <-read_qza('~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/core-metrics_MetaAnalysis_preFMT-1004/weighted_unifrac_distance_matrix.qza')$data


#Partitioning (clustering) of the data into k clusters “around medoids”, a more robust version of K-means.
weightClusterDysbioAdults2 <- pam(myWeightUnipreFMTDM,2, keep.diss = TRUE)
clusterWeightDysbioAdult2 <- pam(myWeightUnipreFMTDM,2, cluster.only = TRUE)

weightClusterDysbioAdults3 <- pam(myWeightUnipreFMTDM,3, keep.diss = TRUE)
clusterWeightDysbioAdult3 <- pam(myWeightUnipreFMTDM,3, cluster.only = TRUE)

weightClusterDysbioAdults4 <- pam(myWeightUnipreFMTDM,4, keep.diss = TRUE)
clusterWeightDysbioAdult4 <- pam(myWeightUnipreFMTDM,4, cluster.only = TRUE)

weightClusterDysbioAdults5 <- pam(myWeightUnipreFMTDM,5, keep.diss = TRUE)
clusterWeightDysbioAdult5 <- pam(myWeightUnipreFMTDM,5, cluster.only = TRUE)

weightClusterDysbioAdults6 <- pam(myWeightUnipreFMTDM,6, keep.diss = TRUE)
clusterWeightDysbioAdult6 <- pam(myWeightUnipreFMTDM,6, cluster.only = TRUE)

weightClusterDysbioAdults7 <- pam(myWeightUnipreFMTDM,7, keep.diss = TRUE)
clusterWeightDysbioAdult7 <- pam(myWeightUnipreFMTDM,7, cluster.only = TRUE)

weightClusterDysbioAdults8 <- pam(myWeightUnipreFMTDM,8, keep.diss = TRUE)
clusterWeightDysbioAdult8 <- pam(myWeightUnipreFMTDM,8, cluster.only = TRUE)

weightClusterDysbioAdults9 <- pam(myWeightUnipreFMTDM,9, keep.diss = TRUE)
clusterWeightDysbioAdult9 <- pam(myWeightUnipreFMTDM,9, cluster.only = TRUE)

weightClusterDysbioAdults10 <- pam(myWeightUnipreFMTDM,10, keep.diss = TRUE)
clusterWeightDysbioAdult10 <- pam(myWeightUnipreFMTDM,10, cluster.only = TRUE)

weightClusterDysbioAdults11 <- pam(myWeightUnipreFMTDM,11, keep.diss = TRUE)
clusterWeightDysbioAdult11 <- pam(myWeightUnipreFMTDM,11, cluster.only = TRUE)

weightClusterDysbioAdults12 <- pam(myWeightUnipreFMTDM,12, keep.diss = TRUE)
clusterWeightDysbioAdult12 <- pam(myWeightUnipreFMTDM,12, cluster.only = TRUE)

weightClusterDysbioAdults13 <- pam(myWeightUnipreFMTDM,13, keep.diss = TRUE)
clusterWeightDysbioAdult13 <- pam(myWeightUnipreFMTDM,13, cluster.only = TRUE)

weightClusterDysbioAdults14 <- pam(myWeightUnipreFMTDM,14, keep.diss = TRUE)
clusterWeightDysbioAdult14 <- pam(myWeightUnipreFMTDM,14, cluster.only = TRUE)

weightClusterDysbioAdults15 <- pam(myWeightUnipreFMTDM,15, keep.diss = TRUE)
clusterWeightDysbioAdult15 <- pam(myWeightUnipreFMTDM,15, cluster.only = TRUE)

weightClusterDysbioAdults16 <- pam(myWeightUnipreFMTDM,16, keep.diss = TRUE)
clusterWeightDysbioAdult16 <- pam(myWeightUnipreFMTDM,16, cluster.only = TRUE)


DysbioCluster2Stats<-ClusteringSummary(weightClusterDysbioAdults2, "Clusters_2",NA,NA,NA,NA)
DysbioCluster3Stats<-ClusteringSummary(weightClusterDysbioAdults3, "Clusters_3",NA,NA,NA,NA)
DysbioCluster4Stats<-ClusteringSummary(weightClusterDysbioAdults4, "Clusters_4",NA,NA,NA,NA)
DysbioCluster5Stats<-ClusteringSummary(weightClusterDysbioAdults5, "Clusters_5",NA,NA,NA,NA)
DysbioCluster6Stats<-ClusteringSummary(weightClusterDysbioAdults6, "Clusters_6",NA,NA,NA,NA)
DysbioCluster7Stats<-ClusteringSummary(weightClusterDysbioAdults7, "Clusters_7",NA,NA,NA,NA)
DysbioCluster8Stats<-ClusteringSummary(weightClusterDysbioAdults8, "Clusters_8",NA,NA,NA,NA)
DysbioCluster9Stats<-ClusteringSummary(weightClusterDysbioAdults9, "Clusters_9",NA,NA,NA,NA)
DysbioCluster10Stats<-ClusteringSummary(weightClusterDysbioAdults10, "Clusters_10",NA,NA,NA,NA)
DysbioCluster11Stats<-ClusteringSummary(weightClusterDysbioAdults11, "Clusters_11",NA,NA,NA,NA)
DysbioCluster12Stats<-ClusteringSummary(weightClusterDysbioAdults12, "Clusters_12",NA,NA,NA,NA)
DysbioCluster13Stats<-ClusteringSummary(weightClusterDysbioAdults13, "Clusters_13",NA,NA,NA,NA)
DysbioCluster14Stats<-ClusteringSummary(weightClusterDysbioAdults14, "Clusters_14",NA,NA,NA,NA)
DysbioCluster15Stats<-ClusteringSummary(weightClusterDysbioAdults15, "Clusters_15",NA,NA,NA,NA)
DysbioCluster16Stats<-ClusteringSummary(weightClusterDysbioAdults16, "Clusters_16",NA,NA,NA,NA)
```
get stats on clustering schemes
```{r, fig.width=13, fig.height =6}
Dysbio2<-DysbioCluster2Stats$DistanceSummary
Dysbio2$DysbioClusters <- "2"
Dysbio3<-DysbioCluster3Stats$DistanceSummary
Dysbio3$DysbioClusters <- "3"
Dysbio4<-DysbioCluster4Stats$DistanceSummary
Dysbio4$DysbioClusters <- "4"
Dysbio5<-DysbioCluster5Stats$DistanceSummary
Dysbio5$DysbioClusters <- "5"
Dysbio6<-DysbioCluster6Stats$DistanceSummary
Dysbio6$DysbioClusters <- "6"
Dysbio7<-DysbioCluster7Stats$DistanceSummary
Dysbio7$DysbioClusters <- "7"
Dysbio8<-DysbioCluster8Stats$DistanceSummary
Dysbio8$DysbioClusters <- "8"
Dysbio9<-DysbioCluster9Stats$DistanceSummary
Dysbio9$DysbioClusters <- "9"
Dysbio10<-DysbioCluster10Stats$DistanceSummary
Dysbio10$DysbioClusters <- "10"
Dysbio11<-DysbioCluster11Stats$DistanceSummary
Dysbio11$DysbioClusters <- "11"
Dysbio12<-DysbioCluster12Stats$DistanceSummary
Dysbio12$DysbioClusters <- "12"
Dysbio13<-DysbioCluster13Stats$DistanceSummary
Dysbio13$DysbioClusters <- "13"
Dysbio14<-DysbioCluster14Stats$DistanceSummary
Dysbio14$DysbioClusters <- "14"
Dysbio15<-DysbioCluster15Stats$DistanceSummary
Dysbio15$DysbioClusters <- "15"
Dysbio16<-DysbioCluster16Stats$DistanceSummary
Dysbio16$DysbioClusters <- "16"

lowList<-c(DysbioCluster2Stats$PercentLowClusters,
           DysbioCluster3Stats$PercentLowClusters,
          DysbioCluster4Stats$PercentLowClusters,
          DysbioCluster5Stats$PercentLowClusters,
          DysbioCluster6Stats$PercentLowClusters,
          DysbioCluster7Stats$PercentLowClusters,
          DysbioCluster8Stats$PercentLowClusters,
          DysbioCluster9Stats$PercentLowClusters,
          DysbioCluster10Stats$PercentLowClusters,
          DysbioCluster11Stats$PercentLowClusters,
          DysbioCluster12Stats$PercentLowClusters,
          DysbioCluster13Stats$PercentLowClusters,
          DysbioCluster14Stats$PercentLowClusters,
          DysbioCluster15Stats$PercentLowClusters,
          DysbioCluster16Stats$PercentLowClusters)

DysbioClusters<-c("2","3","4","5","6",
              "7","8","9","10","11",
              "12","13","14","15","16")

lowTableDysbio<-tibble(DysbioClusters,lowList)

Dysbio2 %>% 
  full_join(Dysbio3) %>% 
  full_join(Dysbio4) %>% 
  full_join(Dysbio5) %>% 
  full_join(Dysbio6) %>% 
  full_join(Dysbio7) %>% 
  full_join(Dysbio8) %>% 
  full_join(Dysbio9) %>% 
  full_join(Dysbio10) %>% 
  full_join(Dysbio11) %>% 
  full_join(Dysbio12) %>% 
  full_join(Dysbio13) %>% 
  full_join(Dysbio14) %>% 
  full_join(Dysbio15)%>% 
  full_join(Dysbio16)->DysbioStats

lowTableDysbio %>% 
  left_join(DysbioStats) ->DysbioSummaryTable

write_tsv(DysbioSummaryTable, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/dysbioLowList_090926.tsv", quote = "none")
#11 has the lower Percent (.18) of clusters with avg sil widths less than 0.1

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/DysbioClusterSummary_082926.pdf", width = 13, height = 11)
DysbioCluster2Stats$SummaryPlot
DysbioCluster6Stats$SummaryPlot
DysbioCluster5Stats$SummaryPlot
DysbioCluster11Stats$SummaryPlot
DysbioCluster12Stats$SummaryPlot
DysbioCluster10Stats$SummaryPlot
DysbioCluster2Stats$ClusterSilPlot
DysbioCluster6Stats$ClusterSilPlot
DysbioCluster5Stats$ClusterSilPlot
DysbioCluster11Stats$ClusterSilPlot
DysbioCluster12Stats$ClusterSilPlot
DysbioCluster10Stats$ClusterSilPlot
DysbioCluster2Stats$RefClusterSilPlot
DysbioCluster6Stats$RefClusterSilPlot
DysbioCluster5Stats$RefClusterSilPlot
DysbioCluster11Stats$RefClusterSilPlot
DysbioCluster12Stats$RefClusterSilPlot
DysbioCluster10Stats$RefClusterSilPlot
DysbioCluster2Stats$RefNighborClusterSilPlot
DysbioCluster11Stats$RefNighborClusterSilPlot
DysbioCluster12Stats$RefNighborClusterSilPlot
DysbioCluster10Stats$RefNighborClusterSilPlot
DysbioCluster6Stats$RefNighborClusterSilPlot
DysbioCluster5Stats$RefNighborClusterSilPlot
dev.off()

allSumSpecifix<-dplyr::bind_rows(DysbioCluster2Stats$SumSpecifics,
                      DysbioCluster3Stats$SumSpecifics,
                      DysbioCluster4Stats$SumSpecifics,
                      DysbioCluster5Stats$SumSpecifics,
                      DysbioCluster6Stats$SumSpecifics,
                      DysbioCluster7Stats$SumSpecifics,
                      DysbioCluster8Stats$SumSpecifics,
                      DysbioCluster9Stats$SumSpecifics,
                      DysbioCluster10Stats$SumSpecifics,
                      DysbioCluster11Stats$SumSpecifics,
                      DysbioCluster12Stats$SumSpecifics,
                      DysbioCluster13Stats$SumSpecifics,
                      DysbioCluster14Stats$SumSpecifics,
                      DysbioCluster15Stats$SumSpecifics,
                      DysbioCluster16Stats$SumSpecifics)

allSumSpecifix$Cluster<-as.factor(allSumSpecifix$Cluster)

allSumSpecifix %>% 
  filter(Scheme == "Clusters_2" | Scheme == "Clusters_11") %>%
  filter(metric != "size") %>% 
  ggplot(aes(x=Cluster, y=unit, fill=Scheme))+
  theme_bw(base_size = 18) +
      labs(tag = "b") +
  geom_bar(stat="identity", position=position_dodge())+
  facet_wrap(~metric, scale = "free_y")+
            scale_fill_discrete(palette = c("grey", "black"))+
  theme(legend.position="none",
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 12),
        axis.title.y = element_text(size = 16),
        axis.text.y = element_text(size = 12),
        legend.margin = margin(t = 0, b = 0, r = 0, l = 0))->SchemeStats
SchemeStats



pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/DysbioSumSpecifics_082926.pdf", width = 13, height = 11)
SchemeStats
dev.off()

rm(Dysbio2, clusterWeightDysbioAdult2, weightClusterDysbioAdults2,
   Dysbio3,DysbioCluster3Stats,clusterWeightDysbioAdult3, weightClusterDysbioAdults3,
   Dysbio4,DysbioCluster4Stats,clusterWeightDysbioAdult4, weightClusterDysbioAdults4,
   Dysbio5,DysbioCluster5Stats,clusterWeightDysbioAdult5, weightClusterDysbioAdults5,
   Dysbio6,DysbioCluster6Stats,clusterWeightDysbioAdult6, weightClusterDysbioAdults6,
   Dysbio7,DysbioCluster7Stats,clusterWeightDysbioAdult7, weightClusterDysbioAdults7,
   Dysbio8,DysbioCluster8Stats,clusterWeightDysbioAdult8, weightClusterDysbioAdults8,
   Dysbio9,DysbioCluster9Stats,clusterWeightDysbioAdult9, weightClusterDysbioAdults9,
   Dysbio10,DysbioCluster10Stats,clusterWeightDysbioAdult10, weightClusterDysbioAdults10,
  Dysbio11,DysbioCluster11Stats,clusterWeightDysbioAdult11, weightClusterDysbioAdults11,
   Dysbio12,DysbioCluster12Stats,clusterWeightDysbioAdult12, weightClusterDysbioAdults12,
   Dysbio13,DysbioCluster13Stats,clusterWeightDysbioAdult13, weightClusterDysbioAdults13,
   Dysbio14,DysbioCluster14Stats,clusterWeightDysbioAdult14, weightClusterDysbioAdults14,
   Dysbio15,DysbioCluster15Stats,clusterWeightDysbioAdult15, weightClusterDysbioAdults15,
   Dysbio16,DysbioCluster16Stats,clusterWeightDysbioAdult16, weightClusterDysbioAdults16
)

print(DysbioSummaryTable)
print(SchemeStats)

DysbioSummaryTable %>% 
  mutate(across(where(is.numeric), round, digits = 2)) %>% 
  relocate(TotalAvgSW, .before = lowList)->SuppFig5SumTb

wrap_table(SuppFig5SumTb, panel = "body", space = "fixed") + SchemeStats ->SuppFig5Top
pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/SuppFig5Top_082926.pdf", width = 11, height = 8.5)
SuppFig5Top
dev.off()
```

After determining 11 is the lowest %, rerun function
```{r}
weightClusterDysbioAdults11 <- pam(myWeightUnipreFMTDM,11, keep.diss = TRUE)
clusterWeightDysbioAdult11 <- pam(myWeightUnipreFMTDM,11, cluster.only = TRUE)
DysbioCluster11Stats<-ClusteringSummary(weightClusterDysbioAdults11, "Clusters_11",NA, NA, 0,0.03)#this one looks good

labelVectorRedo <- setNames(c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, "unClustered"), c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "BTC"))

set.seed(91)
Viridiff <- viridis(555, option = "A") #choose a large number of hexcodes from a color pallette
DysbioColors <- sprintf("%s", sample(Viridiff, 12))
DysbioColors <- setNames(DysbioColors, labelVectorRedo)

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/Dysbio11ClusterSummaryToggle_082926.pdf", width = 13, height = 11)
DysbioCluster11Stats$SummaryPlot
DysbioCluster11Stats$ClusterSilPlot
DysbioCluster11Stats$RefClusterSilPlot
DysbioCluster11Stats$RefNeighborClusterSilPlot
DysbioCluster11Stats$redoneNeighborsSWPlot
dev.off()


DysbioCluster2Stats$SilhouetteTable %>%
  mutate(id = row_number()) %>% 
  ggplot(aes(x=id, y=sil_width))+
  ggtitle("Comparing SWs for 2 Clusters and Neighbor Clusters by Cluster") +
  geom_col(width = 1, fill = "grey")+
  geom_col(data = DysbioCluster11Stats$SilhouetteTable %>%
             arrange(cluster,desc(sil_width)) %>% 
  mutate(id = row_number()),width = 1, fill = "black", alpha =0.8)+
  geom_col(data = DysbioCluster11Stats$redoneNeighborsSWs %>%
             arrange(unNeighborClusters,desc(sil_width)) %>% 
  mutate(id = row_number()),width = 1, fill = "red", alpha =0.7)+
    theme_minimal() +
    theme(
    panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside") + 
    xlab("SimpleID")

DysbioCluster2Stats$SilhouetteTable %>%
  mutate(id = row_number()) %>% 
  ggplot(aes(x=id, y=sil_width))+
  ggtitle("Comparing SWs for 2 Clusters and Neighbor Clusters by Sample SW") +
  geom_col(width = 1, fill = "grey")+
  geom_col(data = DysbioCluster11Stats$SilhouetteTable %>%
             arrange(desc(sil_width)) %>% 
  mutate(id = row_number()),width = 1, fill = "black", alpha =0.8)+
  geom_col(data = DysbioCluster11Stats$redoneNeighborsSWs %>%
             arrange(desc(sil_width)) %>% 
  mutate(id = row_number()),width = 1, fill = "red", alpha =0.7)+
    theme_minimal() +
    theme(
    panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside") + 
    xlab("SimpleID")

```

```{r, fig.width=13, fig.height=5}
DysbioCluster11Stats$SilhouetteTable %>%
  group_by(cluster) %>%
  dplyr::summarise(mean = round(mean(sil_width), digits = 4), n = n()) %>% 
  mutate(label =paste(cluster, "(",n,")", ":", mean))->OrigAvgSil

OrigAvgSil %>% 
   pull(label, name = cluster)->labelOrig

DysbioCluster11Stats$redoneNeighborsSWs %>%
  group_by(unNeighborClusters) %>%
  dplyr::summarise(mean = round(mean(sil_width), digits = 4), n = n()) %>% 
  mutate(label =paste(unNeighborClusters, "(",n,")", ":", mean)) %>% 
  ungroup()->NeighborAvgSil

NeighborAvgSil %>% 
   pull(label, name = unNeighborClusters)->Neighborlabel

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/ComparingClusterSWs_082926.pdf", width = 13, height = 8)
DysbioCluster11Stats$SilhouetteTable %>%
  mutate(id = row_number()) %>% 
  ggplot(aes(fill= cluster, x=id, y=sil_width))+
  geom_col(color = "black", linewidth = 0.13, width = 2)+
  facet_grid(~cluster, switch = "x", scales = "free_x", space = "free_x") +
  discrete_scale(aesthetics = "fill",
               palette = function(x) c(DysbioColors),
               labels = labelOrig)+
    theme_bw(base_size = 18) +
  labs(x = "Samples in Clusters",
       y = "Silhouette Width",
       tag =  "c")+
            theme(legend.position = "right",
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 12),
                axis.title.x = element_text(size = 12),
                axis.text.x = element_blank(),
                axis.tick.x = element_blank(),
                axis.title.y = element_text(size = 12),
                axis.text.y = element_text(size = 10),
                legend.margin = margin(t = 0, b = 0, r = 0, l = 0),
                panel.spacing = unit(0, "lines"), 
                strip.background = element_blank(),
                strip.placement = "outside")+
      scale_y_continuous(limits = c(-0.5,0.6))+
DysbioCluster11Stats$redoneNeighborsSWs %>%
  group_by(unNeighborClusters) %>% 
  arrange(desc(sil_width)) %>% 
  mutate(id = row_number()) %>% 
  ggplot(aes(fill= unNeighborClusters, x=id, y=sil_width))+
  geom_col(color = "black", linewidth = 0.13, width = 2)+
  facet_grid(~unNeighborClusters, switch = "x", scales = "free_x", space = "free_x") +
  discrete_scale(aesthetics = "fill",
               palette = function(x) c(DysbioColors),
               labels = Neighborlabel)+
    theme_bw(base_size = 18) +
  labs(x = "Samples in Clusters",
       y = "Silhouette Width")+
            theme(legend.position = "right",
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 12),
                axis.title.x = element_text(size = 12),
                axis.text.x = element_blank(),
                axis.tick.x = element_blank(),
                axis.title.y = element_text(size = 12),
                axis.text.y = element_text(size = 10),
                legend.margin = margin(t = 0, b = 0, r = 0, l = 0),
                panel.spacing = unit(0, "lines"), 
                strip.background = element_blank(),
                strip.placement = "outside")+
      scale_y_continuous(limits = c(-0.5,0.6))->ComparingSW
ComparingSW
dev.off()
ComparingSW

NeighborStats<- as.tibble(c(
AvgSW= DysbioCluster11Stats$SilhouetteTable%>% 
  dplyr::summarise(mean = mean(sil_width)),
NeighborAvgSW=DysbioCluster11Stats$NeighborClusterNewSW %>% 
  dplyr::summarise(mean = mean(sil_width)),
unNeighborAvgSW=DysbioCluster11Stats$redoneNeighborsSWs%>% 
  dplyr::summarise(mean = mean(sil_width)),
AvgCount = DysbioCluster11Stats$redoneNeighborsSWs %>% 
  group_by(unNeighborClusters) %>% 
  dplyr::summarise(count = n()) %>% 
    ungroup() %>% 
  filter(unNeighborClusters != "unClustered") %>% 
    dplyr::summarise(avgSize = mean(count)),
NeighborNoUnclustAvgSW=DysbioCluster11Stats$NeighborClusterNewSW %>% 
  filter(ReNeighborClusters != "unClustered") %>% 
  dplyr::summarise(mean = mean(sil_width)),
unNeighborNoUnclustAvgSW=DysbioCluster11Stats$redoneNeighborsSWs%>% 
  filter(unNeighborClusters != "unClustered") %>% 
  dplyr::summarise(mean = mean(sil_width))))
#write_tsv(NeighborStats, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/dysbio11AvgSWs_082926.tsv", quote = "none")
print(NeighborStats)
```

going to make a metadata file for Analysis with cluster 11
```{r}
data.table::transpose(bind_rows(clusterWeightDysbioAdult11, .id = 'row'),make.names = 'row', keep.names = 'SampleID') ->myWeightClustersDysbioAdult11
myWeightClustersDysbioAdult11 <- as_tibble(myWeightClustersDysbioAdult11)
colnames(myWeightClustersDysbioAdult11)[2] <- 'Weight11ClusterDysbio'

myWeightRedefClustersDysbio11 <- as_tibble(DysbioCluster11Stats$RedefinedClusters)
colnames(myWeightRedefClustersDysbio11)[2] <- 'ReRefNeighbor11ClusterDysbio'

myWeightNeighborClustersDysbio11 <- as_tibble(DysbioCluster11Stats$RedefinedNeighborClusters)
colnames(myWeightNeighborClustersDysbio11)[2] <- 'Neighbor11ClusterDysbio'

myWeightUnNeighborClustersDysbio11 <- as_tibble(DysbioCluster11Stats$redoneNeighborsSWs)
myWeightUnNeighborClustersDysbio11 %>% 
  select(SampleID,unNeighborClusters)->myWeightUnNeighborClustersDysbio11
 

myWeightClustersDysbioAdult11 %>%
  left_join(myWeightRedefClustersDysbio11) %>% 
  left_join(myWeightNeighborClustersDysbio11)%>% 
  left_join(myWeightUnNeighborClustersDysbio11)->DysbioClusters

DysbioClusters %>% 
  rowid_to_column(var = "ID") %>%
  mutate(SimpleID = paste0("D", ID)) %>% 
  select(-ID)-> DysbioClusters

write_tsv(DysbioClusters, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/11w5DysbioClusters_082926.tsv", quote = "none")

myMeta %>% 
  left_join(DysbioClusters)->FullFMTClusterMeta
write_tsv(FullFMTClusterMeta, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/ReClusters3999Dysbio_metaAnalysis_082926.tsv" , quote = "none")


fullerunWeightUniFullPcoa %>% 
  left_join(DysbioClusters)->unWeightUniPcoaRedefDysbio11
write_tsv(unWeightUniPcoaRedefDysbio11, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/unWeighted3999DysFMTClusters_082926.tsv", quote = "none")

DysbioClusters %>% 
  left_join(fullerunWeightUniFullPcoa)->onlyRedef11DysbioMeta
```

assessing the goodness of this process
```{r}
DysbioCluster11Stats$SilhouetteTable %>% 
  filter(sil_width < 0)->initialNeighbors
nrow(initialNeighbors)
#57
DysbioCluster11Stats$NeighborClusterNewSW %>% 
  filter(sil_width < 0 & ReNeighborClusters != "unClustered")->finalUnClust
nrow(finalUnClust)
#28

DysbioCluster11Stats$lowClustered ->finalUnClust
nrow(finalUnClust)
#48

DysbioCluster11Stats$SilhouetteTable %>% 
  mutate(firstPlacement = case_when(
                            sil_width < NA & sil_width > NA ~ "unClustered",
                            sil_width < 0 ~  "neighbor",
                             TRUE ~ "originalCluster")) ->firstNeighborAssigns
#count the number of samples that get assigned to neighbor, originalCluster, and unClustered in first round
firstNeighborAssigns %>% 
  dplyr::count(firstPlacement)->numberPlacements
print(numberPlacements)
#57 neighbor, 248 originalClusters

#now the new silhouette widths are going to place an additional number of samples into unClustered
DysbioCluster11Stats$NeighborClusterNewSW %>% 
  mutate(secondPlacement = case_when(sil_width < 0.03 & ReNeighborClusters != "unClustered" ~ "unClustered",
                             TRUE ~ "unchanged"))->secondNeighborAssigns

#count the number of samples that get assigned to unClustered in second round and that number added to first neighbor "unClustered" count should equal lowClustered
secondNeighborAssigns %>% 
  dplyr::count(secondPlacement)->number2Placements
print(number2Placements)
#257 unchanged, 48 new Unclustered
firstNeighborAssigns %>% 
  select(SampleID,firstPlacement)->firstPlaceIDs
secondNeighborAssigns %>% 
  select(SampleID,secondPlacement)->secondPlaceIDs

firstPlaceIDs %>% 
  left_join(secondPlaceIDs)->placementAssignments
```

```{r}
#going to add Weighted PCoA data to each subset
myWeightUniPcoaDysbio <-read_qza('~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/core-metrics_MetaAnalysis_preFMT-1004/weighted_unifrac_pcoa_results.qza')$data
#get axis info
WeightUniFullProp <- myWeightUniPcoaDysbio$ProportionExplained[1:4]

#unweighted full prepare axis labels 
WeightDys1_xaxis = paste0('PC1 (', round(WeightUniFullProp [1], 3) * 100, '%)')
WeightDys2_yaxis = paste0('PC2 (', round(WeightUniFullProp [2], 3) * 100, '%)')
WeightDys3_xaxis = paste0('PC3 (', round(WeightUniFullProp [3], 3) * 100, '%)')
WeightDys4_yaxis = paste0('PC4 (', round(WeightUniFullProp [4], 3) * 100, '%)')

#turn them into tibbles and stuff
myWeightUniPcoaDysbio <- as_tibble(myWeightUniPcoaDysbio$Vectors)

colnames(myWeightUniPcoaDysbio)[1] <- 'SampleID'
colnames(myWeightUniPcoaDysbio)[2] <- 'PC1Dys_Wt'
colnames(myWeightUniPcoaDysbio)[3] <- 'PC2Dys_Wt'
colnames(myWeightUniPcoaDysbio)[4] <- 'PC3Dys_Wt'
colnames(myWeightUniPcoaDysbio)[5] <- 'PC4Dys_Wt'

# reducing data if needed
myWeightUniPcoaDysbio %>% 
  select(SampleID,PC1Dys_Wt, PC2Dys_Wt, PC3Dys_Wt, PC4Dys_Wt) ->lessWeighted123PCoADys

rm(myWeightUniPcoaDysbio, WeightUniFullProp)


fullerunWeightUniFullPcoa %>% 
  left_join(lessWeighted123PCoADys) %>% 
  left_join(DysbioClusters, join_by(SampleID))->metaUnWtUniFullSubWtPcoa
```
Distribution stats
```{r, fig.width=18, fig.height=8}
#Dysbio
metaUnWtUniFullSubWtPcoa$Weight11ClusterDysbio <- as.character(metaUnWtUniFullSubWtPcoa$Weight11ClusterDysbio)
metaUnWtUniFullSubWtPcoa$ReRefNeighbor11ClusterDysbio <- as.character(metaUnWtUniFullSubWtPcoa$ReRefNeighbor11ClusterDysbio)
metaUnWtUniFullSubWtPcoa$un<- as.character(metaUnWtUniFullSubWtPcoa$unNeighborClusters)

metaUnWtUniFullSubWtPcoa %>% 
filter(unNeighborClusters != "NA") %>% 
  group_by(target_subfragment) %>%
dplyr::count(unNeighborClusters) ->inforedefinedSubFrag


Viridiff <- viridis(555, option = "A")
set.seed(94)
PrimerColors <- sprintf("%s", sample(Viridiff, 6))
set.seed(91)
DysbioColors <- sprintf("%s", sample(Viridiff, 12))
DysbioColors <- setNames(DysbioColors, labelVectorRedo)
set.seed(99)
StudyColors <- sprintf("%s", sample(Viridiff, 14))
set.seed(94)
HealthColors <- sprintf("%s", sample(Viridiff, 7))

#dysbio
pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/subFragmentByNeighborClusterPlot_082926.pdf", width = 13, height = 11)
inforedefinedSubFrag  %>%   
  ggplot(aes(fill=target_subfragment, y= n, x= unNeighborClusters)) +
  theme_bw(base_size = 18) +
  labs(title = "Samples from Each of 11 Dysbio Clusters",
       subtitle = "By Subfragment",
       x = "Cluster",
       y = "Samples Count",
       tag = "a")+
  geom_bar(position="stack", stat="identity",color = "black", linewidth = 0.3,)+
          discrete_scale(aesthetics = "fill",
               palette = function(x) c(PrimerColors))+
        theme(legend.position = "bottom",
              plot.title = element_text( size = 14),
                plot.subtitle = element_text( size = 12),
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 12),
                axis.title.x = element_text(size = 12),
                axis.text.x = element_text(size = 10),
                axis.title.y = element_text(size = 12),
                axis.text.y = element_text(size = 10),
                legend.margin = margin(t = 0, b = 0, r = 0, l = 0))+
    scale_x_discrete(limits=c(1,2,3,4,5,6,7,8,9,10,11,"unClustered"),
                     labels=labelVectorRedo)->SubFragEffect
SubFragEffect
dev.off()

metaUnWtUniFullSubWtPcoa %>% 
filter(unNeighborClusters != "NA") ->DysbioreRefinedData
  
SubfragData<- table(DysbioreRefinedData$unNeighborClusters, DysbioreRefinedData$target_subfragment)
resultSub <- chisq.test(SubfragData)
print(resultSub)
             
resultSub$expected
cramResultSub<-cramerV(SubfragData)
print(cramResultSub)


metaUnWtUniFullSubWtPcoa %>% 
filter(unNeighborClusters != "NA") %>% 
  group_by(experiment_title) %>%
dplyr::count(unNeighborClusters) ->inforedefinedStudy


pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/studyByNeighborClusterPlot_082926.pdf", width = 13, height = 11)
inforedefinedStudy  %>%   
  ggplot(aes(fill=experiment_title, y= n, x= unNeighborClusters)) +
  theme_bw(base_size = 18) +
  labs(title = "Samples from Each of 11 Dysbio Clusters",
       subtitle = "By Study",
       x = "Cluster",
       y = "Samples Count",
       tag = "b")+
  geom_bar(position="stack", stat="identity",color = "black", linewidth = 0.3,)+
          discrete_scale(aesthetics = "fill",
               palette = function(x) c(StudyColors))+
        theme(legend.position = "bottom",
              plot.title = element_text( size = 14),
                plot.subtitle = element_text( size = 12),
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 12),
                axis.title.x = element_text(size = 12),
                axis.text.x = element_text(size = 10),
                axis.title.y = element_text(size = 12),
                axis.text.y = element_text(size = 10),
                legend.margin = margin(t = 0, b = 0, r = 0, l = 0))+
    scale_x_discrete(limits=c(1,2,3,4,5,6,7,8,9,10,11,"unClustered"),
                     labels=labelVectorRedo)->StudyEffect
StudyEffect
dev.off()


StudyData<- table(DysbioreRefinedData$unNeighborClusters, DysbioreRefinedData$experiment_title)
resultStudy <- chisq.test(StudyData, simulate.p.value = TRUE)
print(resultStudy)
 
resultStudy$expected
cramResultStudy<-cramerV(StudyData)
print(cramResultStudy)



SubFragEffect+StudyEffect->SuppFig6

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/SuppFig6_082926.pdf", width = 11, height = 8.5)
SuppFig6
dev.off()
SuppFig6
```
adonis
```{r}
#dysbio
meta_ordered <- onlyRedef11DysbioMeta[match(rownames(as.matrix(myWeightUnipreFMTDM)), onlyRedef11DysbioMeta$SampleID), ]
#304 PreFMT samples
meta_ordered$experiment_title <- factor(meta_ordered$experiment_title)
meta_ordered$target_subfragment <- factor(meta_ordered$target_subfragment)
meta_ordered$unNeighborClusters <- factor(meta_ordered$unNeighborClusters)

#does cluster explain variation, what do others explain
adonic_result <- adonis2(
                        myWeightUnipreFMTDM ~ target_subfragment + experiment_title + unNeighborClusters,
                        data = meta_ordered,
                        permutations =  999,
                        by = "terms")
#does cluster explain variation after correcting for study
adonic_result2 <- adonis2(
                        myWeightUnipreFMTDM ~ experiment_title + target_subfragment + unNeighborClusters,
                        data = meta_ordered,
                        by = "margin")
DysbioAdonis<-rownames_to_column(adonic_result2, "variable")
#R2 went up to .42 from .38 after neighbors reassignment for Samples, but also putting the 3 samples in cluster 5 in unClustered
#R2 went up to .45 from .42 after neighbors reassignment for SW <0, keeping 5, and then assigning SW<0.03 to unclust
write_tsv(DysbioAdonis, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/Dysbio11NeighborClusterAdonis_082926.tsv", quote = "none")
print(DysbioAdonis)
```

Getting dysbiosis distance info to make placement plot
```{r}
dysbioDist <- read_tsv('~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/MetaSampleDysbioDistances_083126.tsv')

#Attaching dysbio distances onto lotsa meta data
metaUnWtUniFullSubWtPcoa%>% 
  left_join(dysbioDist)->metaUnWtUniFullSubWtPcoaDD

metaUnWtUniFullSubWtPcoaDD %>% 
  filter(unNeighborClusters != 'NA') %>% 
    group_by(unNeighborClusters) %>% 
    summarise(medianDysDist = median(dysbiosis_dist), mean = mean(dysbiosis_dist), 
              minimum = min(dysbiosis_dist), maximum = max(dysbiosis_dist),
              IQR = IQR(dysbiosis_dist), sd = sd(dysbiosis_dist), n = n())-> Dys11DstanceAvgs

#write_tsv(Dys11DstanceAvgs, "~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/Dysbio11w5DistanceSumTab_083126.tsv", quote = "none")

#dysbio 11 redo
centersUnWt<- aggregate(cbind(PC1_UnWt, PC2_UnWt) ~ unNeighborClusters, data=metaUnWtUniFullSubWtPcoaDD, FUN=mean)
centersWt <- aggregate(cbind(PC2Dys_Wt,PC1Dys_Wt) ~ unNeighborClusters, data=metaUnWtUniFullSubWtPcoaDD, FUN=mean)
centersWt %>% 
  left_join(centersUnWt) %>% 
  left_join(Dys11DstanceAvgs)->CentersAvgTabel

colnames(CentersAvgTabel)[2] <- 'PC2Dys_WtAv'
colnames(CentersAvgTabel)[3] <- 'PC1Dys_WtAv'
colnames(CentersAvgTabel)[4] <- 'PC1Dys_UnWtAv'
colnames(CentersAvgTabel)[5] <- 'PC2Dys_UnWtAv'
```


```{r, fig.width=13, fig.height=7}
metaUnWtUniFullSubWtPcoa %>%
  left_join(placementAssignments) %>% 
   ggplot() +
    theme_bw(base_size = 18) +
    xlab(WeightDys1_xaxis) +
    ylab(WeightDys2_yaxis) +
  ggtitle("Weighted Meta-analysis Placement Assignments of Dysbiotic Enterotypes") +
    geom_point(data = metaUnWtUniFullSubWtPcoa %>% 
               filter(unNeighborClusters != "NA"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt,fill = unNeighborClusters),alpha = 0.4, pch = 21, size = 7) +
        discrete_scale(aesthetics = "fill",
               palette = function(x) c(DysbioColors),
                labels = labelVectorRedo)+
              new_scale_fill() +
    geom_point(data = . %>% 
               filter(unNeighborClusters != "NA"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt, fill = firstPlacement), pch = 21, size = 3) +
  scale_fill_discrete(palette = c("black","white"))+
    geom_point(data = . %>% 
               filter(secondPlacement == "unClustered"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt),pch = 21, fill = "red", size = 3)


metaUnWtUniFullSubWtPcoa %>%
  left_join(placementAssignments) %>% 
   ggplot() +
    theme_bw(base_size = 18) +
    xlab(WeightDys1_xaxis) +
    ylab(WeightDys2_yaxis) +
  ggtitle("Weighted Meta-analysis Placement Assignments of Dysbiotic Enterotypes") +
         geom_point(data = CentersAvgTabel %>%
                group_by(unNeighborClusters), 
                aes(y= PC2Dys_WtAv, x= PC1Dys_WtAv, fill=unNeighborClusters),
                    pch = 21, size = 15, alpha = 0.3)+
          discrete_scale(aesthetics = "fill",
               palette = function(x) c(DysbioColors),
                labels = labelVectorRedo)+
    geom_point(data = . %>% 
               filter(unNeighborClusters != "NA"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt, shape = firstPlacement, fill = unNeighborClusters), size = 3, alpha = 0.4) + 
    scale_shape_manual(values=c(25,21,8))+
    geom_point(data = . %>% 
               filter(secondPlacement == "unClustered"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt), color = "red", shape = 4, size = 3)

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/w5NeighborUnclustAssignments_083126.pdf", width = 13, height = 8.5)
metaUnWtUniFullSubWtPcoa %>%
   left_join(placementAssignments) %>% 
    ggplot() +
  labs(title = "Weighted Meta-analysis Placement Assignments",
       x = WeightDys1_xaxis,
       y = WeightDys2_yaxis,
       tag = "b")+
     theme_bw(base_size = 18) +
       geom_point(data = . %>% 
                filter(unNeighborClusters != "NA"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt, shape = firstPlacement), color = "black", stroke =0.3, size = 4.5)+ 
     geom_point(data = . %>% 
                filter(unNeighborClusters != "NA"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt, shape = firstPlacement, color = unNeighborClusters),stroke =1.25, size = 3) + 
         geom_point(data = . %>% 
                filter(unNeighborClusters != "NA"),
               aes(y= PC2Dys_Wt, x= PC1Dys_Wt, shape = firstPlacement), color = "black",stroke =0.3,size = 2.5)+ 
    discrete_scale(aesthetics = "color",
          palette = function(x) c(DysbioColors),
          labels = labelVectorRedo)+
     scale_shape_manual(values=c(25,21,8))+
          theme(legend.position = "right",
              plot.title = element_text( size = 14),
                plot.subtitle = element_text( size = 12),
                legend.text = element_text(size = 10),
                legend.title = element_text(size = 12),
                axis.title.x = element_text(size = 12),
                axis.text.x = element_text(size = 10),
                axis.title.y = element_text(size = 12),
                axis.text.y = element_text(size = 10),
                legend.margin = margin(t = 0, b = 0, r = 0, l = 0))+
     geom_point(data = . %>% 
                filter(secondPlacement == "unClustered"),
                aes(y= PC2Dys_Wt, x= PC1Dys_Wt), color = "red", shape = 4, size = 3)->PlacementFig
PlacementFig
dev.off()
```

```{r, fig.width=15, fig.height=12}

SuppFig5Top/PlacementFig/ComparingSW->SuppFig5

pdf("~/Desktop/Lozupone_022425/Keith/Metaanalysis/metaManuscript/UpdatedData082826/Supp_Fig5_072326.pdf", width = 15, height = 12)
SuppFig5
dev.off()
SuppFig5
```
```{r}
weightClusterDysbioAdults11 <- pam(myWeightUnipreFMTDM,11, keep.diss = TRUE)
weightClusterDysbioAdults11$medoids->medoids11
```
